---
title: "CCC-Process Exploratory Data Analysis"
output:
  html_document:
    toc: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Housekeeping

### R Source Code Available Here:

https://github.com/poorjanos/Work-CCC-Process


### R Session Info
```{r}
sessionInfo()
```


### Load libs
```{r, message = FALSE, echo = TRUE}
library(here)
library(dplyr)
library(ggplot2)
library(purrr)
library(lubridate)
library(scales)
library(tidyr)
library(bupaR)
library(processmapR)
library(DiagrammeR)
```

### Load Data
```{r, cache = TRUE}
t_ccc_pa <- read.csv(here::here("Data" ,"t_ccc_pa_raw_2.csv"), sep = ";", stringsAsFactors = FALSE)

# Transform Data Types Inplace
t_ccc_pa <- t_ccc_pa %>% 
              mutate(EVENT_END = ymd_hms(EVENT_END),
                     CASE_TYPE_PROB_CAT = factor(CASE_TYPE_PROB_CAT))
```

### Variable Descriptions
CASE_ID: unique case identifier  
EVENT_END: end timestamp of event  
USER_ID: identifier of user executing event  
EVENT_CHANNEL: type of event media  
ACTIVITY_HU: event name in hu  
ACTIVITY_EN: event name in en  
CASE_TYPE_HU: contact reason name in hu  
CASE_TYPE_EN: contact reason name in en  
CASE_TYPE_PROB: probability of case type classification  
CASE_TYPE_PROB_CAT: probability of case type classification aggregated to 6 levels  

### Check Data Types
```{r}
purrr::map(t_ccc_pa, typeof)
```

# Cases Overview

### Total Number of Cases
```{r}
t_ccc_pa$CASE_ID %>% unique() %>% length()
```

### Number of Cases by Month
```{r}
t_ccc_pa %>%
  # Transform data
  mutate(EVENT_MONTH = floor_date(EVENT_END, unit = "month")) %>%
  group_by(CASE_ID) %>%
  summarize(CASE_START_MONTH = min(EVENT_MONTH)) %>%
  ungroup() %>%
  group_by(CASE_START_MONTH) %>%
  summarize(COUNT = n()) %>%
  # Plot
  ggplot(aes(x = substr(as.character(CASE_START_MONTH), 1, 7), y = COUNT, group = 1)) +
  geom_line(size = 0.8) +
  theme_minimal() +
  scale_y_continuous(label = unit_format(unit = "K", scale = 1e-3)) +
  theme(axis.text.x = element_text(angle = 90)) +
  labs(
    x = "Month",
    y = "# of Cases",
    title = "Number of Cases per Start Month"
  )
```

### Number of Cases by Case Type
```{r}
t_ccc_pa %>%
  # Transform data
  group_by(CASE_TYPE_EN) %>%
  summarize(COUNT = n_distinct(CASE_ID)) %>%
  ungroup() %>%
  # Plot
  ggplot(
    aes(x = factor(CASE_TYPE_EN, levels = unique(CASE_TYPE_EN[order(COUNT)])), y = COUNT)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  scale_y_continuous(label = unit_format(unit = "K")) +
  coord_flip() +
  labs(
    x = "Case Type",
    y = "# of Cases",
    title = "Number of Cases per Case Type"
  )
```

# Case Type Classification Probabilities

Case types (contact reasons) were determinded by probabilistic methods. Therefore it is good to check how certain one can be about a case belonging to a specific type.


### Distribution of Case Type Probabilites
```{r}
t_ccc_pa %>% 
  # Transform data
  distinct(CASE_ID, CASE_TYPE_PROB) %>% 
  # Plot
  ggplot(aes(CASE_TYPE_PROB)) +
  geom_histogram(bins = 10) +
  theme_minimal() +
  scale_y_continuous(label = unit_format(unit = "K")) +
  labs(
    x = "Case Type Probability",
    y = "# of Cases",
    title = "Distribution of Case Type Probability"
  )
```

### Distribution of Case Type Probabilites by Case Types

The same certainty-check by individual case types.
```{r}
t_ccc_pa %>% 
  # Transform data
  distinct(CASE_ID, CASE_TYPE_EN, CASE_TYPE_PROB) %>% 
  # Plot
  ggplot(
    aes(x = reorder(CASE_TYPE_EN, CASE_ID, FUN = length),
        y = CASE_TYPE_PROB)) +
  geom_boxplot(outlier.shape = NA) +
  theme_minimal() +
  coord_flip() +
  #scale_y_continuous(label = unit_format(unit = "K")) +
  labs(
    y = "Case Type Probability",
    x = "Case Type (Ordered by Case Type Frequency)",
    title = "Distribution of Case Type Probability per Case Type"
  )
```


# Process Structure by Case Type

Each case type is a different contact reason. Thus this part of the analysis is run for case types separately.

```{r, cache = TRUE}
# Add cols to event log required by BupaR
t_ccc_pa_eventlog <- t_ccc_pa %>%
  arrange(CASE_ID, EVENT_END) %>%
  mutate(
    ACTIVITY_INST_ID = as.numeric(row.names(.)),
    LIFECYCLE_ID = "END"
  )


# Define analytics functions
# Trace number
get_trace_num <- function(df){
  number_of_traces(
    eventlog(
           df,
           case_id = "CASE_ID",
           activity_id = "ACTIVITY_EN",
           activity_instance_id = "ACTIVITY_INST_ID",
           lifecycle_id = "LIFECYCLE_ID",
           timestamp = "EVENT_END",
           resource_id = "USER_ID"
           ))
}

# Trace coverage
get_trace_cov <- function(df){
  trace_coverage(
    eventlog(
      df,
      case_id = "CASE_ID",
           activity_id = "ACTIVITY_EN",
           activity_instance_id = "ACTIVITY_INST_ID",
           lifecycle_id = "LIFECYCLE_ID",
           timestamp = "EVENT_END",
           resource_id = "USER_ID"
    ), level = "trace")
}


# Trace lenght aggregates
get_trace_length <- function(df) {
  tidyr::spread(
    data = data.frame(
      metric = c("mean", "median", "min", "max", "st_dev", "q1", "q3", "iqr"),
      values = trace_length(
        eventlog(
          df,
          case_id = "CASE_ID",
           activity_id = "ACTIVITY_EN",
           activity_instance_id = "ACTIVITY_INST_ID",
           lifecycle_id = "LIFECYCLE_ID",
           timestamp = "EVENT_END",
           resource_id = "USER_ID"
        ),
        level = "log", units = "day"
      )[c("mean", "median", "min", "max", "st_dev", "q1", "q3", "iqr")], row.names = NULL
    ),
    key = metric, value = values
  )
}


# Trace lenght by case
get_trace_length_by_case <- function(df) {
  trace_length(
    eventlog(
      df,
      case_id = "CASE_ID",
      activity_id = "ACTIVITY_EN",
      activity_instance_id = "ACTIVITY_INST_ID",
      lifecycle_id = "LIFECYCLE_ID",
      timestamp = "EVENT_END",
      resource_id = "USER_ID"
    ),
    level = "case", units = "day"
  )
}


# Throughput time
get_through_time <- function(df) {
  tidyr::spread(
    data = data.frame(
      metric = c("mean", "median", "min", "max", "st_dev", "q1", "q3"),
      values = throughput_time(
        eventlog(
          df,
          case_id = "CASE_ID",
           activity_id = "ACTIVITY_EN",
           activity_instance_id = "ACTIVITY_INST_ID",
           lifecycle_id = "LIFECYCLE_ID",
           timestamp = "EVENT_END",
           resource_id = "USER_ID"
        ),
        level = "log", units = "day"
      )[c("mean", "median", "min", "max", "st_dev", "q1", "q3")], row.names = NULL
    ),
    key = metric, value = values
  )
}


# Throughput time by case
get_through_time_by_case <- function(df) {
    throughput_time(
      eventlog(
        df,
        case_id = "CASE_ID",
        activity_id = "ACTIVITY_EN",
        activity_instance_id = "ACTIVITY_INST_ID",
        lifecycle_id = "LIFECYCLE_ID",
        timestamp = "EVENT_END",
        resource_id = "USER_ID"
      ),
      level = "case", units = "day"
    )
}


# Genarate nested df
# Gen nested tables with aggregated stats in nested tables
by_case_type <- t_ccc_pa_eventlog %>%
  group_by(CASE_TYPE_EN) %>%
  nest() %>%
  mutate(
    CASE_NUMBER = map(data, ~length(unique(.$CASE_ID))),
    EVENT_NUMBER = map(data, ~length(unique(.$ACTIVITY_EN))),
    TRACE_NUMBER = map(data, get_trace_num),
    TRACE_COV = map(data, get_trace_cov),
    TRACE_LENGTH_AGGREGATE = map(data, get_trace_length),
    TRACE_LENGTH_BY_CASE = map(data, get_trace_length_by_case),
    THROUGH_TIME_AGGREGATE = map(data, get_through_time),
    THROUGH_TIME_BY_CASE = map(data, get_through_time_by_case)
  )
```

### Trace Number

High variability of traces detected for each contact reason. 

```{r}
by_case_type %>% select(CASE_TYPE_EN, CASE_NUMBER, TRACE_NUMBER) %>%
  unnest() %>% 
  ggplot(aes(
    x = factor(CASE_TYPE_EN, levels = unique(CASE_TYPE_EN[order(CASE_NUMBER)])), 
    y = absolute)) +
    geom_bar(stat = "identity") +
    theme_minimal() +
    scale_y_continuous(label = unit_format(unit = "K")) +
    coord_flip() +
    labs(
      x = "Case Type (Ordered by Case Type Frequency)",
      y = "# of Unique Traces",
      title = "Number of Unique Traces per Case Type "
    )
```

### Trace Coverage

Despite high variability of traces it is only a small subset of traces that cover the majority of cases (strong Pareto effect). Traces are thus noisy, but there are a few strong patterns underneath.

```{r}
by_case_type %>% select(CASE_TYPE_EN, TRACE_COV) %>% 
  unnest() %>% 
  group_by(CASE_TYPE_EN) %>%
  mutate(RNUM = row_number()) %>%
  ungroup() %>% 
  ggplot(aes(x = RNUM, y = cum_sum)) +
      geom_line() +
      theme_minimal() +
      theme(axis.text.x = element_text(angle = 90)) +
      coord_cartesian(xlim = c(0, 500)) +
      facet_wrap(~CASE_TYPE_EN, ncol = 4) +
      labs(
          x = "Unique traces",
          y = "Coverage (Cumulative Perentage)",
          title = "Trace Coverage Per Case Type"
        )
```


### Trace Length
```{r}
by_case_type %>% select(CASE_TYPE_EN, TRACE_LENGTH_BY_CASE) %>%
  unnest() %>%
  ggplot(
    aes(x = reorder(CASE_TYPE_EN, CASE_ID, FUN = length),
        y = trace_length)) +
  geom_boxplot(outlier.shape = NA) +
  theme_minimal() +
  coord_flip(ylim = c(0,10)) +
  scale_y_continuous(breaks=seq(0,10,1)) +
  labs(
    y = "Number of Activities",
    x = "Case Type (Ordered by Case Type Frequency)",
    title = "Distribution of Trace Length per Case Type"
  )
```

### Throughput Time
```{r}
by_case_type %>% select(CASE_TYPE_EN, THROUGH_TIME_BY_CASE) %>%
  unnest() %>%
  ggplot(
    aes(x = reorder(CASE_TYPE_EN, CASE_ID, FUN = length),
        y = throughput_time)) +
  geom_boxplot(outlier.shape = NA) +
  theme_minimal() +
  coord_flip(ylim = c(0,50)) +
  scale_y_continuous(breaks=seq(0,50,5)) +
  labs(
    y = "Throughput Time (day)",
    x = "Case Type (Ordered by Case Type Frequency)",
    title = "Distribution of Throughput Time per Case Type"
  )
```

