---
title: "Contact Center: Top 3 Requests Overview"
output:
  html_document:
    toc: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, message=FALSE,}
library(here)
library(dplyr)
library(ggplot2)
library(purrr)
library(lubridate)
library(scales)
library(tidyr)
library(bupaR)
library(processmapR)
library(DiagrammeR)
```

```{r, message=FALSE}
t_ccc_pa <- read.csv(here::here("Data" ,"t_ccc_pa_top3.csv"), sep = ";", stringsAsFactors = FALSE)

# Transform Data Types Inplace
t_ccc_pa <- t_ccc_pa %>%
  mutate(EVENT_END = ymd_hms(EVENT_END)) %>% 
  filter(EVENT_END < as.Date('2019-01-01'))
  
```

# Introduction

The Contact Center identified three major request types at the expert sessions on 5 March:  
* Claim report
* Contract termination
* Provide information

The Advanced Analytics Team delivers:
* Process maps further cleaned
* etc



### Identify the Biggest Volumes: Number of Cases by Month
```{r}
t_ccc_pa %>%
  # Transform data
  filter(PRODUCT_LINE != "UNKNOWN") %>% 
  mutate(EVENT_MONTH = floor_date(EVENT_END, unit = "month")) %>%
  group_by(CASE_ID, CASE_TYPE_EN, PRODUCT_LINE) %>%
  summarize(CASE_START_MONTH = min(EVENT_MONTH)) %>%
  ungroup() %>%
  group_by(CASE_START_MONTH, CASE_TYPE_EN, PRODUCT_LINE) %>%
  summarize(COUNT = n()) %>%
  # Plot
  ggplot(aes(x = substr(as.character(CASE_START_MONTH), 1, 7), y = COUNT, group = 1)) +
  geom_line(size = 0.8) +
  scale_y_continuous(label = unit_format(unit = "K", scale = 1e-3)) +
  theme(axis.text.x = element_text(angle = 90, size = 6)) +
  facet_grid(CASE_TYPE_EN~PRODUCT_LINE) +
  labs(
    x = "Month",
    y = "# of Cases",
    title = "Number of Cases per Start Month"
  )
```

***


# Process Structure by Case Type

Each case type is a different contact reason. Thus this part of the analysis is run for case types separately.

```{r, cache = TRUE}
# Add cols to event log required by BupaR
t_ccc_pa_eventlog <- t_ccc_pa %>%
  arrange(CASE_ID, EVENT_END) %>%
  mutate(
    ACTIVITY_INST_ID = as.numeric(row.names(.)),
    LIFECYCLE_ID = "END"
  )


# Define analytics functions
# Trace number
get_trace_num <- function(df){
  number_of_traces(
    eventlog(
           df,
           case_id = "CASE_ID",
           activity_id = "ACTIVITY_EN",
           activity_instance_id = "ACTIVITY_INST_ID",
           lifecycle_id = "LIFECYCLE_ID",
           timestamp = "EVENT_END",
           resource_id = "USER_ID"
           ))
}

# Trace coverage
get_trace_cov <- function(df){
  trace_coverage(
    eventlog(
      df,
      case_id = "CASE_ID",
           activity_id = "ACTIVITY_EN",
           activity_instance_id = "ACTIVITY_INST_ID",
           lifecycle_id = "LIFECYCLE_ID",
           timestamp = "EVENT_END",
           resource_id = "USER_ID"
    ), level = "trace")
}


# Trace lenght aggregates
get_trace_length <- function(df) {
  tidyr::spread(
    data = data.frame(
      metric = c("mean", "median", "min", "max", "st_dev", "q1", "q3", "iqr"),
      values = trace_length(
        eventlog(
          df,
          case_id = "CASE_ID",
           activity_id = "ACTIVITY_EN",
           activity_instance_id = "ACTIVITY_INST_ID",
           lifecycle_id = "LIFECYCLE_ID",
           timestamp = "EVENT_END",
           resource_id = "USER_ID"
        ),
        level = "log", units = "day"
      )[c("mean", "median", "min", "max", "st_dev", "q1", "q3", "iqr")], row.names = NULL
    ),
    key = metric, value = values
  )
}


# Trace lenght by case
get_trace_length_by_case <- function(df) {
  trace_length(
    eventlog(
      df,
      case_id = "CASE_ID",
      activity_id = "ACTIVITY_EN",
      activity_instance_id = "ACTIVITY_INST_ID",
      lifecycle_id = "LIFECYCLE_ID",
      timestamp = "EVENT_END",
      resource_id = "USER_ID"
    ),
    level = "case", units = "day"
  )
}


# Throughput time
get_through_time <- function(df) {
  tidyr::spread(
    data = data.frame(
      metric = c("mean", "median", "min", "max", "st_dev", "q1", "q3"),
      values = throughput_time(
        eventlog(
          df,
          case_id = "CASE_ID",
           activity_id = "ACTIVITY_EN",
           activity_instance_id = "ACTIVITY_INST_ID",
           lifecycle_id = "LIFECYCLE_ID",
           timestamp = "EVENT_END",
           resource_id = "USER_ID"
        ),
        level = "log", units = "day"
      )[c("mean", "median", "min", "max", "st_dev", "q1", "q3")], row.names = NULL
    ),
    key = metric, value = values
  )
}


# Throughput time by case
get_through_time_by_case <- function(df) {
    throughput_time(
      eventlog(
        df,
        case_id = "CASE_ID",
        activity_id = "ACTIVITY_EN",
        activity_instance_id = "ACTIVITY_INST_ID",
        lifecycle_id = "LIFECYCLE_ID",
        timestamp = "EVENT_END",
        resource_id = "USER_ID"
      ),
      level = "case", units = "day"
    )
}


# Genarate nested df
# Gen nested tables with aggregated stats in nested tables
by_case_type <- t_ccc_pa_eventlog %>%
  group_by(CASE_TYPE_EN) %>%
  nest() %>%
  mutate(
    CASE_NUMBER = map(data, ~length(unique(.$CASE_ID))),
    EVENT_NUMBER = map(data, ~length(unique(.$ACTIVITY_EN))),
    TRACE_NUMBER = map(data, get_trace_num),
    TRACE_COV = map(data, get_trace_cov),
    TRACE_LENGTH_AGGREGATE = map(data, get_trace_length),
    TRACE_LENGTH_BY_CASE = map(data, get_trace_length_by_case),
    THROUGH_TIME_AGGREGATE = map(data, get_through_time),
    THROUGH_TIME_BY_CASE = map(data, get_through_time_by_case)
  )
```

### Trace Number per Case Type

High variability of traces detected for each contact reason. 

```{r}
by_case_type %>% select(CASE_TYPE_EN, CASE_NUMBER, TRACE_NUMBER) %>%
  unnest() %>% 
  ggplot(aes(
    x = factor(CASE_TYPE_EN, levels = unique(CASE_TYPE_EN[order(CASE_NUMBER)])), 
    y = absolute)) +
    geom_bar(stat = "identity") +
    theme_minimal() +
    scale_y_continuous(label = unit_format(unit = "K")) +
    coord_flip() +
    labs(
      x = "Case Type (Ordered by Case Type Frequency)",
      y = "# of Unique Traces",
      title = "Number of Unique Traces per Case Type "
    )
```

### Trace Coverage per Case Type

Despite high variability of traces it is only a small subset of traces that cover the majority of cases (strong Pareto effect). Traces are thus noisy, but there are a few strong patterns underneath.

```{r}
by_case_type %>% select(CASE_TYPE_EN, TRACE_COV) %>% 
  unnest() %>% 
  group_by(CASE_TYPE_EN) %>%
  mutate(RNUM = row_number()) %>%
  ungroup() %>% 
  ggplot(aes(x = RNUM, y = cum_sum)) +
      geom_line() +
      theme_minimal() +
      theme(axis.text.x = element_text(angle = 90)) +
      coord_cartesian(xlim = c(0, 500)) +
      facet_wrap(~CASE_TYPE_EN, ncol = 4) +
      labs(
          x = "Unique traces",
          y = "Coverage (Cumulative Perentage)",
          title = "Trace Coverage Per Case Type"
        )
```


### Trace Length per Case Type

```{r}
by_case_type %>% select(CASE_TYPE_EN, TRACE_LENGTH_BY_CASE) %>%
  unnest() %>%
  ggplot(
    aes(x = reorder(CASE_TYPE_EN, CASE_ID, FUN = length),
        y = trace_length)) +
  geom_boxplot(outlier.shape = NA) +
  theme_minimal() +
  coord_flip(ylim = c(0,10)) +
  scale_y_continuous(breaks=seq(0,10,1)) +
  labs(
    y = "Number of Activities",
    x = "Case Type (Ordered by Case Type Frequency)",
    title = "Distribution of Trace Length per Case Type"
  )
```

### Throughput Time Distribution
```{r}
by_case_type %>% select(CASE_TYPE_EN, THROUGH_TIME_BY_CASE) %>%
  unnest() %>%
  ggplot(
    aes(throughput_time)) +
  geom_histogram(bins = 500) +
  coord_cartesian(xlim = c(0,50)) +
  theme_minimal() +
  scale_y_continuous(label = unit_format(unit = "K")) +
  labs(
    y = "# of Cases",
    x = "Throughput Time (days)",
    title = "Distribution of Throughput Time"
  )
```

### Throughput Time per Case Type
```{r}
by_case_type %>% select(CASE_TYPE_EN, THROUGH_TIME_BY_CASE) %>%
  unnest() %>%
  ggplot(
    aes(x = reorder(CASE_TYPE_EN, CASE_ID, FUN = length),
        y = throughput_time)) +
  geom_boxplot(outlier.shape = NA) +
  theme_minimal() +
  coord_flip(ylim = c(0,50)) +
  scale_y_continuous(breaks=seq(0,50,5)) +
  labs(
    y = "Throughput Time (day)",
    x = "Case Type (Ordered by Case Type Frequency)",
    title = "Distribution of Throughput Time per Case Type"
  )
```

### Throughput Time By Month
```{r}
case_month <- t_ccc_pa_eventlog %>% 
  group_by(CASE_ID) %>%
  summarize(START_MONTH = floor_date(min(EVENT_END), unit="months")) %>% 
  ungroup()

by_case_type %>% select(CASE_TYPE_EN, THROUGH_TIME_BY_CASE) %>%
  unnest() %>%
  left_join(case_month, by = "CASE_ID") %>% 
  group_by(START_MONTH) %>% 
  summarize(THROUGHPUT_TIME_MEDIAN = median(throughput_time),
             THROUGHPUT_TIME_AVG = mean(throughput_time)) %>% 
  ungroup() %>%
  ggplot(
    aes(x = START_MONTH,
        y = THROUGHPUT_TIME_MEDIAN)) +
  geom_line() +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90)) +
  labs(
    y = "Throughput Time (day)",
    x = "Month",
    title = "Median Distribution of Throughput Time by Month"
  )
```

### Throughput Time per Case Type By Month
```{r}
by_case_type %>% select(CASE_TYPE_EN, THROUGH_TIME_BY_CASE) %>%
  unnest() %>%
  left_join(case_month, by = "CASE_ID") %>% 
  group_by(START_MONTH,  CASE_TYPE_EN) %>% 
  summarize(THROUGHPUT_TIME_MEDIAN = median(throughput_time),
             THROUGHPUT_TIME_AVG = mean(throughput_time)) %>% 
  ungroup() %>% 
  ggplot(
    aes(x = START_MONTH,
        y = THROUGHPUT_TIME_MEDIAN)) +
  geom_line() +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90)) +
  facet_wrap(~CASE_TYPE_EN, ncol = 4, scales = "free") +
  labs(
    y = "Throughput Time (day)",
    x = "Month",
    title = "Median Distribution of Throughput Time per Case Type by Month"
  )
```