---
title: "Contact Center: Call Times and FTE"
author: "János Poór"
date: 'May 17, 2019'
output: rmdformats::readthedown
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, message=FALSE, warning=FALSE}
library(here)
library(dplyr)
library(ggplot2)
library(lubridate)
library(scales)
library(tidyr)
library(ggrepel)
```

```{r, message=FALSE, include=FALSE}
#########################################################################################
# Data Extraction #######################################################################
#########################################################################################

# Set JAVA_HOME, set max. memory, and load rJava library
Sys.setenv(JAVA_HOME = "C:\\Program Files\\Java\\jre1.8.0_171")
options(java.parameters = "-Xmx2g")
library(rJava)

# Output Java version
.jinit()
print(.jcall("java/lang/System", "S", "getProperty", "java.version"))

# Load RJDBC library
library(RJDBC)

# Get credentials
datamnr <-
  config::get("datamnr", file = "C:\\Users\\PoorJ\\Projects\\config.yml")

# Create connection driver
jdbcDriver <-
  JDBC(driverClass = "oracle.jdbc.OracleDriver", classPath = "C:\\Users\\PoorJ\\Desktop\\ojdbc7.jar")

# Open connection: kontakt---------------------------------------------------------------
jdbcConnection <-
  dbConnect(
    jdbcDriver,
    url = datamnr$server,
    user = datamnr$uid,
    password = datamnr$pwd
  )

# Fetch data
t_call_times <- dbGetQuery(jdbcConnection, 'select * from t_call_times')
t_mnap <- dbGetQuery(jdbcConnection, 'select * from t_mnap')

# Close db connection: kontakt
dbDisconnect(jdbcConnection)


# Transformations
t_call_times <- t_call_times %>%
  mutate(EVENT_END = ymd_hms(EVENT_END)) %>%
  filter(EVENT_END < as.Date("2019-01-01")) %>%
  replace_na(list(PRODUCT_LINE = "UNKNOWN", PRODUCT_CODE = "UNKNOWN", CASE_TYPE_EN = "UNKNOWN"))

t_call_times[t_call_times$CASE_TYPE_EN == "Delete contract", "CASE_TYPE_EN"] <- "Contract termination"

t_call_times[ t_call_times$ACTIVITY_EN == "!Delete contract", "ACTIVITY_EN"] <- "Delete contract"

t_call_times[t_call_times$CASE_TYPE_EN == "Claim report" &
  t_call_times$ACTIVITY_EN %in% c("Provide information Property assignments", "Provide information Motor vehicle claim report") &
  startsWith(t_call_times$CASE_ID, "S"), "ACTIVITY_EN"] <- "Provide information NOT on claim file"

t_call_times[t_call_times$CASE_TYPE_EN == "Claim report" &
  t_call_times$ACTIVITY_EN %in% c("Provide information Property assignments", "Provide information Motor vehicle claim report") &
  startsWith(t_call_times$CASE_ID, "K"), "ACTIVITY_EN"] <- "Provide information on claim file"

t_call_times[t_call_times$ACTIVITY_EN %in%
               c("Request claim recording", "Claim report (request inspection)"), "ACTIVITY_EN"] <- "Report claim"

t_mnap <- t_mnap %>% mutate(IDOSZAK = ymd_hms(IDOSZAK))
```

# 1. Introduction and Glossary

Incoming calls represent the biggest workload of the Contact Center. This analysis provides insights to the amount of human resources spent on incoming calls by connecting call duration data (from TCT) with process-specific metainformaton (from Kontakt).

Glossary of terms:  

* Call Volume: number of calls in period
* FTE: Full-time-equivalent computed for one month
* Cost (per call): Normalized FTE - Full-time-equivalent computed for 1000 calls for one month


# 2. Call Volumes and FTE

```{r}
t_call_times %>%
  # Transform data
  #filter(PRODUCT_LINE != "UNKNOWN") %>% 
  mutate(EVENT_MONTH = floor_date(EVENT_END, unit = "month")) %>%
  group_by(EVENT_MONTH) %>%
  summarize(CALL_VOLUME = n(),
            CALL_TIME_SEC = sum(CALL_TIME)) %>%
  ungroup() %>%
  left_join(t_mnap, by = c("EVENT_MONTH" = "IDOSZAK")) %>% 
  mutate(FTE = CALL_TIME_SEC/60/60/7/MNAP,
         COST = FTE/CALL_VOLUME*1000) %>%
  select(EVENT_MONTH, CALL_VOLUME, FTE, COST) %>% 
  tidyr::gather(key = METRIC, value = VALUE, -EVENT_MONTH) %>%
  mutate(METRIC = factor(METRIC, levels = c("CALL_VOLUME", "FTE", "COST"))) %>% 
  # Plot
  ggplot(aes(x = substr(as.character(EVENT_MONTH), 1, 7), y = VALUE, group = 1)) +
  geom_line() +
  theme(axis.text.x = element_text(angle = 90)) +
  facet_grid(METRIC~., scales = "free") +
  labs(
    x = "Month",
    y = "Value",
    title = "Call Volumes and FTE"
  )
```


***

# 3. Understanding FTE across Request Types & Products

## 3.1. Breakdown of Volumes and FTE across Request Types

```{r, fig.width=14, fig.height=10}
t_call_times %>%
  # Transform data
  filter(PRODUCT_LINE != "UNKNOWN") %>% 
  mutate(EVENT_MONTH = floor_date(EVENT_END, unit = "month"),
         EVENT_QUARTER = paste0(year(EVENT_END), " q", quarter(EVENT_END)), 
         CASE_TYPE_EN = forcats::fct_lump(factor(CASE_TYPE_EN), n = 7),
         SEGMENT = CASE_TYPE_EN) %>%
  group_by(EVENT_MONTH, EVENT_QUARTER, SEGMENT) %>%
  summarize(CALL_VOLUME = n(),
            CALL_TIME_SEC = sum(CALL_TIME)) %>%
  ungroup() %>%
  left_join(t_mnap, by = c("EVENT_MONTH" = "IDOSZAK")) %>% 
  group_by(EVENT_QUARTER, SEGMENT) %>% 
  summarize(CALL_VOLUME = sum(CALL_VOLUME),
            CALL_TIME_SEC = sum(CALL_TIME_SEC),
            MNAP = sum(MNAP)) %>% 
  ungroup() %>% 
  mutate(FTE = CALL_TIME_SEC/60/60/7/MNAP,
         COST = FTE*3/CALL_VOLUME*1000) %>%
  select(EVENT_QUARTER, SEGMENT, CALL_VOLUME, FTE, COST) %>% 
  tidyr::gather(key = METRIC, value = VALUE, -EVENT_QUARTER, -SEGMENT) %>% 
  mutate(METRIC = factor(METRIC, levels = c("CALL_VOLUME", "FTE", "COST"))) %>% 
  # Plot
  ggplot(aes(x = substr(as.character(EVENT_QUARTER), 1, 7), y = VALUE, group = 1)) +
  geom_line() +
  theme(axis.text.x = element_text(angle = 90),
        strip.text.x = element_text(angle=90),
        strip.text.y = element_text(angle=0)) +
  facet_grid(METRIC~SEGMENT, scales = "free") +
  labs(
    x = "Month",
    y = "Value",
    title = "Call Volumes and FTE by Request Types (Quarterly Trends)"
  )
```


## 3.2. Breakdown of Volumes and FTE across Request Types & Products

```{r, fig.width=14, fig.height=10}
t_call_times %>%
  # Transform data
  filter(PRODUCT_LINE != "UNKNOWN") %>% 
  mutate(EVENT_MONTH = floor_date(EVENT_END, unit = "month"),
         EVENT_QUARTER = paste0(year(EVENT_END), " q", quarter(EVENT_END)), 
         CASE_TYPE_EN = forcats::fct_lump(factor(CASE_TYPE_EN), n = 7),
         SEGMENT = paste(CASE_TYPE_EN, PRODUCT_LINE)) %>%
  group_by(EVENT_MONTH, EVENT_QUARTER, SEGMENT) %>%
  summarize(CALL_VOLUME = n(),
            CALL_TIME_SEC = sum(CALL_TIME)) %>%
  ungroup() %>%
  left_join(t_mnap, by = c("EVENT_MONTH" = "IDOSZAK")) %>% 
  group_by(EVENT_QUARTER, SEGMENT) %>% 
  summarize(CALL_VOLUME = sum(CALL_VOLUME),
            CALL_TIME_SEC = sum(CALL_TIME_SEC),
            MNAP = sum(MNAP)) %>% 
  ungroup() %>% 
  mutate(FTE = CALL_TIME_SEC/60/60/7/MNAP,
         COST = FTE*3/CALL_VOLUME*1000) %>%
  select(EVENT_QUARTER, SEGMENT, CALL_VOLUME, FTE, COST) %>% 
  tidyr::gather(key = METRIC, value = VALUE, -EVENT_QUARTER, -SEGMENT) %>% 
  mutate(METRIC = factor(METRIC, levels = c("CALL_VOLUME", "FTE", "COST"))) %>% 
  # Plot
  ggplot(aes(x = substr(as.character(EVENT_QUARTER), 1, 7), y = VALUE, group = 1)) +
  geom_line() +
  theme(axis.text.x = element_text(angle = 90, size = 6),
        strip.text.x = element_text(angle=90),
        strip.text.y = element_text(angle=0)) +
  facet_grid(METRIC~SEGMENT, scales = "free") +
  labs(
    x = "Month",
    y = "Value",
    title = "Call Volumes and FTE by Request Types and Product (Quarterly Trends)"
  )
```

***


# 4. FTE Impact Map


## 4.1. Impact Map: Identify Processes that Cosume Most FTE

Gross FTE is the product of two factors: 

* Call volume: number of calls in period
* Cost per call: cost of one call (measured by normalized FTE for 1000 calls)

The impact map represents FTE consumption by ball-size. Additionally it gives insight into how that FTE is genereated. The same amount of FTE can be due to different reasons. For example:  

* High call volume with low call per cost
* Low call volume with high call per cost

> A business case can target either of the above factors.

```{r, include = FALSE}
t_call_times %>%
  # Transform data
  filter(PRODUCT_LINE != "UNKNOWN",
         EVENT_END >= as.Date('2018-01-01')) %>% 
  mutate(EVENT_MONTH = floor_date(EVENT_END, unit = "month"),
         #CASE_TYPE_EN = forcats::fct_lump(factor(CASE_TYPE_EN), n = 7),
         SEGMENT = forcats::fct_lump(paste(CASE_TYPE_EN, PRODUCT_LINE), n = 13, other_level = "Everything else")) %>%
  group_by(EVENT_MONTH,  SEGMENT) %>%
  summarize(CALL_VOLUME = n(),
            CALL_TIME_SEC = sum(CALL_TIME)) %>%
  ungroup() %>%
  left_join(t_mnap, by = c("EVENT_MONTH" = "IDOSZAK")) %>% 
  mutate(FTE = CALL_TIME_SEC/60/60/7/MNAP,
         COST = FTE/CALL_VOLUME*1000) %>%
  # Compute monthly averages
  group_by(SEGMENT) %>% 
  summarize(
            CALL_VOLUME = mean(CALL_VOLUME),
            FTE = mean(FTE),
            COST = mean(COST)) %>% 
  # Plot
  ggplot(aes(x = CALL_VOLUME, y = COST, label = SEGMENT)) +
    geom_point(aes(size = FTE), colour = "blue") +
    geom_label_repel(aes(label = SEGMENT),
                  box.padding   = 0.2, 
                  point.padding = 0.5,
                  segment.color = 'grey50') +
    #coord_cartesian(ylim = c(0, 4.5)) +
    labs(
      x = "Calls (Monthly Average)",
    y = "Cost (Normalized FTE for 1000 calls)",
    title = "FTE Impact Map of Calls"
    )
```

```{r, include = TRUE}
t_call_times %>%
  # Transform data
  filter(PRODUCT_LINE != "UNKNOWN",
         EVENT_END >= as.Date('2018-01-01')) %>% 
  mutate(EVENT_MONTH = floor_date(EVENT_END, unit = "month"),
         #CASE_TYPE_EN = forcats::fct_lump(factor(CASE_TYPE_EN), n = 7),
         SEGMENT = forcats::fct_lump(paste(CASE_TYPE_EN, PRODUCT_LINE), n = 8, other_level = "Everything else")) %>%
  group_by(EVENT_MONTH,  SEGMENT) %>%
  summarize(CALL_VOLUME = n(),
            CALL_TIME_SEC = sum(CALL_TIME)) %>%
  ungroup() %>%
  left_join(t_mnap, by = c("EVENT_MONTH" = "IDOSZAK")) %>% 
  mutate(FTE = CALL_TIME_SEC/60/60/7/MNAP,
         COST = FTE/CALL_VOLUME*1000) %>%
  # Compute monthly averages
  group_by(SEGMENT) %>% 
  summarize(
            CALL_VOLUME = mean(CALL_VOLUME),
            FTE = mean(FTE),
            COST = mean(COST)) %>%
  filter(SEGMENT != "Everything else") %>% 
  # Plot
  ggplot(aes(x = CALL_VOLUME, y = COST, label = SEGMENT)) +
    geom_point(aes(size = FTE), colour = "blue") +
    geom_label_repel(aes(label = SEGMENT),
                  box.padding   = 0.1, 
                  point.padding = 0.6,
                  segment.color = 'grey50') +
    #coord_cartesian(ylim = c(0, 4.5)) +
    labs(
      x = "Calls (Monthly Average)",
    y = "Cost per Call (Normalized FTE)",
    title = "Impact Map of Processes"
    )
```

```{r, include = FALSE}
t_call_times %>%
  # Transform data
  filter(PRODUCT_LINE != "UNKNOWN",
         EVENT_END >= as.Date('2018-01-01')) %>% 
  mutate(EVENT_MONTH = floor_date(EVENT_END, unit = "month"),
         #CASE_TYPE_EN = forcats::fct_lump(factor(CASE_TYPE_EN), n = 7),
         SEGMENT = forcats::fct_lump(paste(CASE_TYPE_EN, PRODUCT_LINE), n = 8, other_level = "Everything else")) %>%
  group_by(EVENT_MONTH,  SEGMENT) %>%
  summarize(CALL_VOLUME = n(),
            CALL_TIME_SEC = sum(CALL_TIME)) %>%
  ungroup() %>%
  left_join(t_mnap, by = c("EVENT_MONTH" = "IDOSZAK")) %>% 
  mutate(FTE = CALL_TIME_SEC/60/60/7/MNAP,
         COST = FTE/CALL_VOLUME*1000) %>%
  # Compute monthly averages
  group_by(SEGMENT) %>% 
  summarize(
            CALL_VOLUME = mean(CALL_VOLUME),
            FTE = mean(FTE),
            COST = mean(COST)) %>%
  filter(SEGMENT != "Everything else") %>% 
  # Plot
  ggplot(aes(x = CALL_VOLUME, y = FTE, label = SEGMENT)) +
    geom_point(aes(size = COST), colour = "blue") +
    geom_label_repel(aes(label = SEGMENT),
                  box.padding   = 0.1, 
                  point.padding = 0.6,
                  segment.color = 'grey50') +
    #coord_cartesian(ylim = c(0, 4.5)) +
    labs(
      x = "Calls (Monthly Average)",
    y = "FTE",
    title = "Impact Map of Processes"
    )
```

```{r, include = FALSE}
t_call_times %>%
  # Transform data
  filter(PRODUCT_LINE != "UNKNOWN",
         EVENT_END >= as.Date('2018-01-01')) %>% 
  mutate(EVENT_MONTH = floor_date(EVENT_END, unit = "month"),
         #CASE_TYPE_EN = forcats::fct_lump(factor(CASE_TYPE_EN), n = 7),
         SEGMENT = forcats::fct_lump(paste(CASE_TYPE_EN, PRODUCT_LINE), n = 8, other_level = "Everything else")) %>%
  group_by(EVENT_MONTH,  SEGMENT) %>%
  summarize(CALL_VOLUME = n(),
            CALL_TIME_SEC = sum(CALL_TIME)) %>%
  ungroup() %>%
  left_join(t_mnap, by = c("EVENT_MONTH" = "IDOSZAK")) %>% 
  mutate(FTE = CALL_TIME_SEC/60/60/7/MNAP,
         COST = FTE/CALL_VOLUME*1000) %>%
  # Compute monthly averages
  group_by(SEGMENT) %>% 
  summarize(
            CALL_VOLUME = mean(CALL_VOLUME),
            FTE = mean(FTE),
            COST = mean(COST)) %>%
  filter(SEGMENT != "Everything else") %>% 
  # Plot
  ggplot(aes(x = FTE, y = COST, label = SEGMENT)) +
    geom_point(aes(size = CALL_VOLUME), colour = "blue") +
    geom_label_repel(aes(label = SEGMENT),
                  box.padding   = 0.1, 
                  point.padding = 0.6,
                  segment.color = 'grey50') +
    #coord_cartesian(ylim = c(0, 4.5)) +
    labs(
      x = "FTE",
    y = "Cost",
    title = "Impact Map of Processes"
    )
```


## 4.2. Understand the Root-Causes of FTE comsumption

### 4.2.1. Understand the Root-Causes of FTE comsumption

The FTE of each process can be broken by call type. Call type is the service or solution provided for the customer in the call.

Note the other category can broken down for further call types if neccessary.

```{r, fig.width=14, fig.height=14}
t_call_times %>%
  # Transform data
  filter(PRODUCT_LINE != "UNKNOWN",
         EVENT_END >= as.Date('2018-01-01')) %>% 
  mutate(EVENT_MONTH = floor_date(EVENT_END, unit = "month"),
         #CASE_TYPE_EN = forcats::fct_lump(factor(CASE_TYPE_EN), n = 7),
         SEGMENT = forcats::fct_lump(paste(CASE_TYPE_EN, PRODUCT_LINE), n = 13)) %>%
  group_by(EVENT_MONTH, SEGMENT) %>% 
  mutate(ACTIVITY_EN = as.character(forcats::fct_lump(ACTIVITY_EN, prop = 0.05))) %>% 
  ungroup() %>% 
  group_by(EVENT_MONTH, SEGMENT, ACTIVITY_EN) %>%
  summarize(CALL_VOLUME = n(),
            CALL_TIME_SEC = sum(CALL_TIME)) %>%
  ungroup() %>%
  left_join(t_mnap, by = c("EVENT_MONTH" = "IDOSZAK")) %>% 
  mutate(FTE = CALL_TIME_SEC/60/60/7/MNAP,
         COST = FTE/CALL_VOLUME*1000) %>%
  # Compute monthly averages
  group_by(SEGMENT, ACTIVITY_EN) %>% 
  summarize(
            CALL_VOLUME = mean(CALL_VOLUME),
            FTE = mean(FTE),
            COST = mean(COST)) %>% 
  tidyr::gather(-SEGMENT, -ACTIVITY_EN, key = METRIC, value = VALUE) %>% 
  mutate(METRIC = factor(METRIC, levels = c("CALL_VOLUME", "FTE", "COST"))) %>% 
  # Plot
  ggplot(aes(x = ACTIVITY_EN, y = VALUE)) +
    geom_bar(stat = "identity") +
    theme(strip.text.y = element_text(angle=0)) +
    coord_flip() +
    facet_grid(SEGMENT~METRIC, scales = "free") +
    labs(
      x = "Calls types",
    y = "Values",
    title = "Call Types Comparison"
    )
```


### 4.2.2. Compare FTE of Processes with Biggest Impact

```{r, fig.width=10}
t_call_times %>%
  # Transform data
  filter(PRODUCT_LINE != "UNKNOWN",
         EVENT_END >= as.Date('2018-01-01')) %>% 
  mutate(EVENT_MONTH = floor_date(EVENT_END, unit = "month"),
         #CASE_TYPE_EN = forcats::fct_lump(factor(CASE_TYPE_EN), n = 7),
         SEGMENT = forcats::fct_lump(paste(CASE_TYPE_EN, PRODUCT_LINE), n = 13)) %>%
  group_by(EVENT_MONTH, SEGMENT) %>% 
  mutate(ACTIVITY_EN = as.character(forcats::fct_lump(ACTIVITY_EN, prop = 0.05))) %>% 
  ungroup() %>% 
  group_by(EVENT_MONTH, SEGMENT, ACTIVITY_EN) %>%
  summarize(CALL_VOLUME = n(),
            CALL_TIME_SEC = sum(CALL_TIME)) %>%
  ungroup() %>%
  left_join(t_mnap, by = c("EVENT_MONTH" = "IDOSZAK")) %>% 
  mutate(FTE = CALL_TIME_SEC/60/60/7/MNAP,
         COST = FTE/CALL_VOLUME*1000) %>%
  # Compute monthly averages
  group_by(SEGMENT, ACTIVITY_EN) %>% 
  summarize(
            CALL_VOLUME = mean(CALL_VOLUME),
            FTE = mean(FTE),
            COST = mean(COST)) %>%
  ungroup() %>% 
  filter(SEGMENT %in% c('Claim report HOUSE', 'Claim report CAR', 'Provide information CAR', 'Provide information HOUSE')) %>% 
  select(SEGMENT, ACTIVITY_EN, FTE) %>% 
  mutate(SEGMENT = forcats::fct_relevel(SEGMENT, 'Claim report HOUSE', 'Claim report CAR',
                                        'Provide information CAR', 'Provide information HOUSE')) %>%
  mutate(ACTIVITY_EN = forcats::fct_reorder(ACTIVITY_EN, FTE, sum)) %>% 
  mutate(ACTIVITY_EN = forcats::fct_relevel(ACTIVITY_EN, "Other")) %>% 
  #tidyr::gather(-SEGMENT, -ACTIVITY_EN, key = METRIC, value = VALUE) %>% 
  #mutate(METRIC = factor(METRIC, levels = c("CALL_VOLUME", "FTE", "COST"))) %>% 
  # Plot
  ggplot(aes(x = ACTIVITY_EN, y = FTE)) +
    geom_bar(stat = "identity") +
    theme(strip.text.y = element_text(angle=0)) +
    coord_flip() +
    facet_grid(.~SEGMENT, labeller = label_wrap_gen(width=10)) +
    labs(
      x = "Call types",
    y = "FTE",
    title = "Call Types Comparison"
    )
```



### 4.2.3. Show Request Types with Highest Wrap-up FTE

Total FTE can be broken down to  

* speak-time FTE
* wrap-up FTE

> 29% of FTE is spent on wrap-ups. 


```{r}
t_call_times %>%
  # Transform data
  filter(PRODUCT_LINE != "UNKNOWN",
         EVENT_END >= as.Date('2018-01-01')) %>% 
  mutate(EVENT_MONTH = floor_date(EVENT_END, unit = "month"),
         #CASE_TYPE_EN = forcats::fct_lump(factor(CASE_TYPE_EN), n = 7),
         SEGMENT = forcats::fct_lump(paste(CASE_TYPE_EN, PRODUCT_LINE), n = 13, other_level = "Everything else")) %>%
  group_by(EVENT_MONTH,  SEGMENT) %>%
  summarize(
        CALL_VOLUME = n(),
        CALL_TIME_SEC = sum(CALL_TIME),
        SPEAK_TIME_SEC = sum(SPEAK_TIME),
        WRAPUP_TIME_SEC = sum(WRAPUP_TIME)) %>%
  ungroup() %>%
  left_join(t_mnap, by = c("EVENT_MONTH" = "IDOSZAK")) %>% 
  mutate(
    FTE = CALL_TIME_SEC/60/60/7/MNAP,
    COST = FTE/CALL_VOLUME*1000,
    SPEAK_FTE = SPEAK_TIME_SEC/60/60/7/MNAP,
    SPEAK_COST = SPEAK_FTE/CALL_VOLUME*1000,
    WRAPUP_FTE = WRAPUP_TIME_SEC/60/60/7/MNAP,
    WRAPUP_COST = WRAPUP_FTE/CALL_VOLUME*1000) %>%
  # Compute monthly averages
  group_by(SEGMENT) %>% 
  summarize(
            CALL_VOLUME = mean(CALL_VOLUME),
            FTE = mean(FTE),
            COST = mean(COST),
            SPEAK_FTE = mean(SPEAK_FTE),
            SPEAK_COST = mean(SPEAK_COST),
            WRAPUP_FTE = mean(WRAPUP_FTE),
            WRAPUP_COST = mean(WRAPUP_COST)) %>% 
  ungroup() %>% 
  mutate(WRAPUP_RATIO = WRAPUP_FTE/FTE) %>% 
  mutate(SEGMENT = forcats::fct_reorder(SEGMENT, WRAPUP_RATIO, sum)) %>% 
  mutate(SEGMENT = forcats::fct_relevel(SEGMENT, "Everything else")) %>% 
  # Plot
  ggplot(aes(x = SEGMENT, y = WRAPUP_RATIO)) +
    geom_bar(stat = "identity") +
    scale_y_continuous(label = percent) +
    coord_flip() +
    labs(
      x = "Request Type",
    y = "Ratio of Wrap-up FTE to Total FTE",
    title = "Proprotion of FTE Spent on Wrap-up"
    )
```


### 4.2.4. Call per request

```{r}
t_call_times %>%
  # Transform data
  filter(PRODUCT_LINE != "UNKNOWN",
         EVENT_END >= as.Date('2018-01-01')) %>% 
  mutate(EVENT_MONTH = floor_date(EVENT_END, unit = "month"),
         #CASE_TYPE_EN = forcats::fct_lump(factor(CASE_TYPE_EN), n = 7),
         SEGMENT = forcats::fct_lump(paste(CASE_TYPE_EN, PRODUCT_LINE), n = 13, other_level = "Everything else")) %>%
  group_by(EVENT_MONTH,  SEGMENT, CASE_ID) %>%
  summarize(
        CALL_VOLUME = n()) %>%
  ungroup() %>%
  group_by(SEGMENT) %>% 
  summarize(CALL_PER_REQUEST = mean(CALL_VOLUME)) %>% 
  ungroup() %>% 
  mutate(SEGMENT = forcats::fct_reorder(SEGMENT, CALL_PER_REQUEST, sum)) %>% 
  mutate(SEGMENT = forcats::fct_relevel(SEGMENT, "Everything else")) %>% 
  # Plot
  ggplot(aes(x = SEGMENT, y = CALL_PER_REQUEST)) +
    geom_bar(stat = "identity") +
    coord_flip(ylim = c(1, 1.5)) +
    labs(
      x = "Request Type",
    y = "Calls per Request",
    title = "Average Number of Calls on a Single Request"
    )
```