---
title: "CCC Wrap Ups - Prune Decision Trees"
author: "János Poór"
date: 'April 2, 2019'
output: rmdformats::readthedown
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, message = FALSE, echo = TRUE, include=FALSE}
library(config)
library(dplyr)
library(ggplot2)
library(lubridate)
library(scales)
library(tidyr)
```

```{r, include=FALSE}
# Data Extraction #######################################################################

# Set JAVA_HOME, set max. memory, and load rJava library
Sys.setenv(JAVA_HOME = "C:\\Program Files\\Java\\jre1.8.0_171")
options(java.parameters = "-Xmx2g")
library(rJava)

# Output Java version
.jinit()
print(.jcall("java/lang/System", "S", "getProperty", "java.version"))

# Load RJDBC library
library(RJDBC)

# Get credentials
datamnr <-
  config::get("datamnr", file = "C:\\Users\\PoorJ\\Projects\\config.yml")

# Create connection driver
jdbcDriver <-
  JDBC(driverClass = "oracle.jdbc.OracleDriver", classPath = "C:\\Users\\PoorJ\\Desktop\\ojdbc7.jar")

# Open connection: kontakt
jdbcConnection <-
  dbConnect(
    jdbcDriver,
    url = datamnr$server,
    user = datamnr$uid,
    password = datamnr$pwd
  )

# Fetch data
query_actions <- "
SELECT   intezkedes,
           cnt,
           ratio,
           SUM (ratio) OVER (ORDER BY ratio DESC) AS running_ratio
    FROM   (SELECT   intezkedes, cnt, cnt / SUM (cnt) OVER () AS ratio
              FROM   (  SELECT   DISTINCT intezkedes, SUM (cnt) AS cnt
                          FROM   (  SELECT   mm,
                                             alirattipus,
                                             f_wf,
                                             intezkedes,
                                             SUM (cnt) AS cnt
                                      FROM   mesterr.pa_intezkedes_crunch
                                     WHERE       alirattipus IS NOT NULL
                                             AND f_wf IS NOT NULL
                                             AND intezkedes IS NOT NULL
                                             AND f_wf = '_CCC_Intézkedés'
                                  GROUP BY   mm,
                                             alirattipus,
                                             f_wf,
                                             intezkedes
                                  ORDER BY   2,
                                             3,
                                             4,
                                             1)
                      GROUP BY   intezkedes
                      ORDER BY   2 DESC))
ORDER BY   ratio DESC
"
t_actions <- dbGetQuery(jdbcConnection, query_actions)

query_actions_per_doctype <- "
  SELECT   alirattipus,
           intezkedes,
           cnt,
           ratio,
           SUM (ratio) OVER (PARTITION BY alirattipus ORDER BY ratio DESC)
              AS running_ratio
    FROM   (SELECT   alirattipus,
                     intezkedes,
                     cnt,
                     cnt / SUM (cnt) OVER (PARTITION BY alirattipus) AS ratio
              FROM   (  SELECT   DISTINCT
                                 alirattipus, intezkedes, SUM (cnt) AS cnt
                          FROM   (  SELECT   mm,
                                             alirattipus,
                                             f_wf,
                                             intezkedes,
                                             SUM (cnt) AS cnt
                                      FROM   mesterr.pa_intezkedes_crunch
                                     WHERE       alirattipus IS NOT NULL
                                             AND f_wf IS NOT NULL
                                             AND intezkedes IS NOT NULL
                                             AND f_wf = '_CCC_Intézkedés'
                                  GROUP BY   mm,
                                             alirattipus,
                                             f_wf,
                                             intezkedes
                                  ORDER BY   2,
                                             3,
                                             4,
                                             1)
                      GROUP BY   alirattipus, intezkedes
                      ORDER BY   1, 3 DESC))
ORDER BY   alirattipus, ratio DESC
"
t_actions_doctype <- dbGetQuery(jdbcConnection, query_actions_per_doctype)

# Close db connection: kontakt
dbDisconnect(jdbcConnection)
```

# Wrap Up Leaf Nodes and Request Types

Total count of wrap-up leaf nodes is 532. There is great variance of the leaf node count across the 212 requeset types.

```{r}
t_actions_doctype %>% group_by(ALIRATTIPUS) %>%
  summarize(LEAF_NODE_CNT = n()) %>% 
  arrange(desc(LEAF_NODE_CNT)) %>% 
  ungroup() %>% 
ggplot(aes(x = factor(ALIRATTIPUS, levels = unique(ALIRATTIPUS[order(LEAF_NODE_CNT)])),
           y = LEAF_NODE_CNT)) +
  geom_bar(stat = "identity") +
  theme(axis.text.y = element_text(size = 2)) +
  coord_flip() +
  labs(
    title = "Wrap Up Leaf Node Count by Request Type",    
    y = "# of Wrap Up Leaf Nodes",
    x = "Request Type"
      )
```

# Distribution of Wrap Up Leaf Nodes Occurance

Over half of the available leaf nodes are almost never used. Only about 10% of all leaf nodes are in frequent usage.

```{r}
t_actions %>%
  ggplot() +
  geom_bar(aes(x = factor(INTEZKEDES, levels = unique(INTEZKEDES[order(RATIO, decreasing = TRUE)])), y = RATIO),
           stat = "identity") +
  geom_line(aes(x = factor(INTEZKEDES, levels = unique(INTEZKEDES[order(RATIO, decreasing = TRUE)])), y = RUNNING_RATIO, group = 1)) +
  theme(axis.text.x = element_text(size = 2, angle = 90)) +
  labs(
    title = "Occurance Ratio of Wrap Up Leaf Nodes",    
    y = "Occurance Ratio of Wrap Up Leaf Nodes",
    x = "Request Type"
      )
```

# Close-up on Ration of Occurance 

511 of the 532 leaf nodes are used in less then 1% of cases.

```{r}
t_actions %>% 
  mutate(RATIO_CUT = cut(RATIO, seq(0,1, 0.01))) %>% 
  group_by(RATIO_CUT) %>% 
  summarize(CNT = n()) %>% 
  ggplot(aes(x = RATIO_CUT, y = CNT)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label=CNT), vjust=-0.3, size=3.5) +
  labs(
    title = "Probability Categories of Occurance",    
    y = "# of Wrap Up Leaf Nodes",
    x = "Occurance Ratio Bins"
      )
  
```

# Toplist of Least Used Leaf Nodes

Most useless nodes are the ones that are present in many trees (request types) and have a very low probability of orrurance in all of them: maximum probablity of occurance less than 1%. 

```{r}
knitr::kable(t_actions_doctype %>%
  group_by(INTEZKEDES) %>%
  summarize(
    PRESENT_IN = n(),
    MEDIAN_OCCURANCE_PROB = round(median(RATIO), 4),
    MIN_OCCURANCE_PROB = round(min(RATIO), 4),
    MAX_OCCURANCE_PROB = round(max(RATIO), 4),
    SPAN_OCCURANCE_PROB = round(abs(MIN_OCCURANCE_PROB - MAX_OCCURANCE_PROB), 4)
  ) %>%
  ungroup() %>%
  filter(MAX_OCCURANCE_PROB < 0.01) %>%
  arrange(desc(PRESENT_IN), SPAN_OCCURANCE_PROB) %>%
  transmute(
    LEAF_NODE = INTEZKEDES,
    PRESENT_IN = PRESENT_IN,
    MEDIAN = scales::percent(MEDIAN_OCCURANCE_PROB),
    MIN = scales::percent(MIN_OCCURANCE_PROB),
    MAX = scales::percent(MAX_OCCURANCE_PROB),
    SPAN = scales::percent(SPAN_OCCURANCE_PROB)
  ), caption = "Toplist of Least Used Leaf Nodes Based on Occurance Probabilites")
```