---
title: "Contact Center: Call Times and FTE 2018-2019 Comparison"
author: "János Poór"
date: "`r Sys.Date()`"
output: rmdformats::readthedown
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, message=FALSE, warning=FALSE}
library(here)
library(dplyr)
library(ggplot2)
library(lubridate)
library(scales)
library(tidyr)
library(ggrepel)
library(stringr)
```

```{r, message=FALSE, include=FALSE}
#########################################################################################
# Data Extraction #######################################################################
#########################################################################################

# Set JAVA_HOME, set max. memory, and load rJava library
Sys.setenv(JAVA_HOME = "C:\\Program Files\\Java\\jre1.8.0_171")
options(java.parameters = "-Xmx2g")
library(rJava)

# Output Java version
.jinit()
print(.jcall("java/lang/System", "S", "getProperty", "java.version"))

# Load RJDBC library
library(RJDBC)

# Get credentials
datamnr <-
  config::get("datamnr", file = "C:\\Users\\PoorJ\\Projects\\config.yml")

# Create connection driver
jdbcDriver <-
  JDBC(driverClass = "oracle.jdbc.OracleDriver", classPath = "C:\\Users\\PoorJ\\Desktop\\ojdbc7.jar")

# Open connection: kontakt---------------------------------------------------------------
jdbcConnection <-
  dbConnect(
    jdbcDriver,
    url = datamnr$server,
    user = datamnr$uid,
    password = datamnr$pwd
  )

# Fetch data
t_call_times <- dbGetQuery(jdbcConnection, 'select * from t_call_times UNION select * from t_call_times_2019')
t_mnap <- dbGetQuery(jdbcConnection, 'select * from t_mnap')

# Close db connection: kontakt
dbDisconnect(jdbcConnection)


# Transformations
t_call_times <- t_call_times %>%
  mutate(EVENT_END = ymd_hms(EVENT_END)) %>%
  #filter(EVENT_END < as.Date("2019-01-01")) %>%
  replace_na(list(PRODUCT_LINE = "UNKNOWN", PRODUCT_CODE = "UNKNOWN", CASE_TYPE_EN = "UNKNOWN"))

t_call_times[t_call_times$CASE_TYPE_EN == "Delete contract", "CASE_TYPE_EN"] <- "Contract termination"

t_call_times[ t_call_times$ACTIVITY_EN == "!Delete contract", "ACTIVITY_EN"] <- "Delete contract"

t_call_times[t_call_times$CASE_TYPE_EN == "Claim report" &
  t_call_times$ACTIVITY_EN %in% c("Provide information Property assignments", "Provide information Motor vehicle claim report") &
  startsWith(t_call_times$CASE_ID, "S"), "ACTIVITY_EN"] <- "Provide information NOT on claim file"

t_call_times[t_call_times$CASE_TYPE_EN == "Claim report" &
  t_call_times$ACTIVITY_EN %in% c("Provide information Property assignments", "Provide information Motor vehicle claim report") &
  startsWith(t_call_times$CASE_ID, "K"), "ACTIVITY_EN"] <- "Provide information on claim file"

t_call_times[t_call_times$ACTIVITY_EN %in%
               c("Request claim recording", "Claim report (request inspection)"), "ACTIVITY_EN"] <- "Report claim"

t_mnap <- t_mnap %>% mutate(IDOSZAK = ymd_hms(IDOSZAK))
```


# 1. KPIs: Call Volumes, FTE and Cost

Incoming calls represent the biggest workload of the Contact Center. This analysis provides insights to the amount of human resources spent on incoming calls by connecting call duration data (from TCT) with process-specific metainformaton (from Kontakt).

Glossary of terms:  

* Call Volume: number of calls in period
* FTE: Full-time-equivalent computed for one month
* Cost (per call): Normalized FTE - Full-time-equivalent computed for 1000 calls for one month

```{r}
t_call_times %>%
  # Transform data
  #filter(PRODUCT_LINE != "UNKNOWN") %>% 
  mutate(EVENT_MONTH = floor_date(EVENT_END, unit = "month")) %>%
  group_by(EVENT_MONTH) %>%
  summarize(CALL_VOLUME = n(),
            CALL_TIME_SEC = sum(CALL_TIME)) %>%
  ungroup() %>%
  left_join(t_mnap, by = c("EVENT_MONTH" = "IDOSZAK")) %>% 
  mutate(FTE = CALL_TIME_SEC/60/60/7/MNAP,
         COST = FTE/CALL_VOLUME*1000) %>%
  select(EVENT_MONTH, CALL_VOLUME, FTE, COST) %>% 
  tidyr::gather(key = METRIC, value = VALUE, -EVENT_MONTH) %>%
  mutate(METRIC = factor(METRIC, levels = c("CALL_VOLUME", "FTE", "COST")),
         YEAR = factor(lubridate::year(EVENT_MONTH)),
         MONTH = lubridate::month(EVENT_MONTH)) %>% 
  # Plot
  ggplot(aes(x = MONTH, y = VALUE, group = YEAR, colour = YEAR)) +
  geom_line() +
  scale_x_continuous(breaks = seq(12)) +
  theme(axis.text.x = element_text(angle = 90)) +
  facet_grid(METRIC~., scales = "free") +
  labs(
    x = "Month",
    y = "Value",
    title = "Call Volumes and FTE"
  )
```


<!-- ## 1.1. Trends by Request Type -->

```{r, fig.width=12, include= FALSE}
t_call_times %>%
  # Transform data
  filter(PRODUCT_LINE != "UNKNOWN") %>%
  filter(PRODUCT_LINE != 'LIFE') %>% 
  mutate(EVENT_MONTH = floor_date(EVENT_END, unit = "month"),
         CASE_TYPE_EN = forcats::fct_lump(factor(CASE_TYPE_EN), n = 7),
         SEGMENT = paste(CASE_TYPE_EN, PRODUCT_LINE)) %>%
  group_by(EVENT_MONTH, SEGMENT) %>%
  summarize(CALL_VOLUME = n(),
            CALL_TIME_SEC = sum(CALL_TIME)) %>%
  ungroup() %>%
  left_join(t_mnap, by = c("EVENT_MONTH" = "IDOSZAK")) %>% 
  group_by(EVENT_MONTH, SEGMENT) %>% 
  summarize(CALL_VOLUME = sum(CALL_VOLUME),
            CALL_TIME_SEC = sum(CALL_TIME_SEC),
            MNAP = sum(MNAP)) %>% 
  ungroup() %>% 
  mutate(FTE = CALL_TIME_SEC/60/60/7/MNAP,
         COST = FTE/CALL_VOLUME*1000) %>%
  select(EVENT_MONTH, SEGMENT, CALL_VOLUME, FTE, COST) %>% 
  tidyr::gather(key = METRIC, value = VALUE, -EVENT_MONTH, -SEGMENT) %>% 
  mutate(METRIC = factor(METRIC, levels = c("CALL_VOLUME", "FTE", "COST")),
         YEAR = factor(lubridate::year(EVENT_MONTH)),
         MONTH = lubridate::month(EVENT_MONTH)) %>%
  #filter(SEGMENT == "Claim report HOUSE") %>% 
  # Plot
  ggplot(aes(x = MONTH, y = VALUE, group = YEAR, colour = YEAR)) +
  geom_line() +
  scale_x_continuous(breaks = seq(12)) +
  theme(axis.text.x = element_text(angle = 0, size = 4),
        strip.text.x = element_text(angle=90),
        strip.text.y = element_text(angle=0)) +
  facet_grid(METRIC~SEGMENT, scales = "free") +
  labs(
    x = "Month",
    y = "Value",
    title = "Call Volumes and FTE by Request Types and Product"
  )
```

***


# 2. FTE Impact Map

Gross FTE is the product of two factors: 

* Call volume: number of calls in period
* Cost per call: cost of one call (measured by normalized FTE for 1000 calls)

The impact map represents FTE consumption by ball-size. Additionally it gives insight into how that FTE is genereated. The same amount of FTE can be due to different reasons. For example:  

* High call volume with low call per cost
* Low call volume with high call per cost

> A business case can target either of the above factors.

```{r, include = TRUE, fig.width=10}
t_call_times %>%
  # Transform data
  filter(PRODUCT_LINE != "UNKNOWN") %>% 
  filter(
    (EVENT_END >= as.Date('2018-01-01') & EVENT_END < as.Date('2018-06-01')) |
    (EVENT_END >= as.Date('2019-01-01') & EVENT_END < as.Date('2019-06-01'))
         ) %>%
  mutate(YEAR = paste("Jan-May", lubridate::year(EVENT_END))) %>% 
  mutate(EVENT_MONTH = floor_date(EVENT_END, unit = "month"),
         #CASE_TYPE_EN = forcats::fct_lump(factor(CASE_TYPE_EN), n = 7),
         SEGMENT = forcats::fct_lump(paste(CASE_TYPE_EN, PRODUCT_LINE), n = 9, other_level = "Everything else")) %>%
  group_by(YEAR, EVENT_MONTH,  SEGMENT) %>%
  summarize(CALL_VOLUME = n(),
            CALL_TIME_SEC = sum(CALL_TIME)) %>%
  ungroup() %>%
  left_join(t_mnap, by = c("EVENT_MONTH" = "IDOSZAK")) %>% 
  mutate(FTE = CALL_TIME_SEC/60/60/7/MNAP,
         COST = FTE/CALL_VOLUME*1000) %>%
  # Compute monthly averages
  group_by(YEAR, SEGMENT) %>% 
  summarize(
            CALL_VOLUME = mean(CALL_VOLUME),
            FTE = mean(FTE),
            COST = mean(COST)) %>%
  filter(SEGMENT != "Everything else") %>% 
  arrange(YEAR, desc(FTE)) %>% 
  # Plot
  ggplot(aes(x = CALL_VOLUME, y = COST, label = SEGMENT)) +
    geom_point(aes(size = FTE), colour = "blue") +
    geom_label_repel(aes(label = SEGMENT),
                  box.padding   = 0.35, 
                  point.padding = 0.5,
                  segment.color = 'grey50',
                  force = 50,
                  size = 3.5) +
    facet_grid(.~YEAR) +
    coord_cartesian(ylim = c(0.7, 1.025)) +
    labs(
      x = "Calls (Monthly Average)",
    y = "Cost per Call (Normalized FTE)",
    title = "Impact Map of Processes"
    )
```


## 2.1. Absolute KPI Change 2018-2019

```{r, include = TRUE, fig.width=10}
# Define function to use tidyr::spread for multiple value columns
myspread <- function(df, key, value) {
  # quote key
  keyq <- rlang::enquo(key)
  # break value vector into quotes
  valueq <- rlang::enquo(value)
  s <- rlang::quos(!!valueq)
  df %>%
    gather(variable, value, !!!s) %>%
    unite(temp, variable, !!keyq) %>%
    spread(temp, value)
}


t_call_times %>%
  # Transform data
  filter(PRODUCT_LINE != "UNKNOWN") %>%
  filter(
    (EVENT_END >= as.Date("2018-01-01") & EVENT_END < as.Date("2018-06-01")) |
      (EVENT_END >= as.Date("2019-01-01") & EVENT_END < as.Date("2019-06-01"))
  ) %>%
  mutate(YEAR = lubridate::year(EVENT_END)) %>%
  mutate(
    EVENT_MONTH = floor_date(EVENT_END, unit = "month"),
    SEGMENT = forcats::fct_lump(paste(CASE_TYPE_EN, PRODUCT_LINE), n = 9, other_level = "Everything else")
  ) %>%
  group_by(YEAR, EVENT_MONTH, SEGMENT) %>%
  summarize(
    CALL_VOLUME = n(),
    CALL_TIME_SEC = sum(CALL_TIME)
  ) %>%
  ungroup() %>%
  left_join(t_mnap, by = c("EVENT_MONTH" = "IDOSZAK")) %>%
  mutate(
    FTE = CALL_TIME_SEC / 60 / 60 / 7 / MNAP,
    COST = FTE / CALL_VOLUME * 1000
  ) %>%
  # Compute monthly averages
  group_by(YEAR, SEGMENT) %>%
  summarize(
    CALL_VOLUME = mean(CALL_VOLUME),
    FTE = mean(FTE),
    COST = mean(COST)
  ) %>%
  filter(SEGMENT != "Everything else") %>%
  arrange(YEAR, desc(FTE)) %>%
  myspread(YEAR, c(CALL_VOLUME, FTE, COST)) %>%
  mutate(
    VOLUME = CALL_VOLUME_2019 / CALL_VOLUME_2018 - 1,
    FTE = FTE_2019 / FTE_2018 - 1,
    COST = COST_2019 / COST_2018 - 1
  ) %>%
  mutate(SEGMENT = forcats::fct_rev(forcats::fct_reorder(SEGMENT, desc(FTE_2019)))) %>%
  select(SEGMENT, VOLUME, FTE, COST) %>%
  tidyr::gather(METRIC, VALUE, -SEGMENT) %>%
  mutate(METRIC = forcats::fct_relevel(METRIC, "VOLUME", "FTE", "COST")) %>%
  # Plot
  ggplot(aes(x = SEGMENT, VALUE)) +
  geom_bar(aes(fill = VALUE < 0), stat = "identity") +
  scale_fill_manual(guide = FALSE, breaks = c(TRUE, FALSE), values = c("#FF6347", "#90EE90")) +
  scale_y_continuous(labels = percent) +
  geom_hline(yintercept = 0, colour = "#A9A9A9", linetype = "longdash") +
  coord_flip(ylim = c(-0.5, 0.5)) +
  facet_grid(. ~ METRIC) +
  labs(
    x = "Contact Reason",
    y = "Rate of Change (%)",
    title = "KPIs: Absolute Change 2018-2019 (Jan-May)"
  )
```


## 2.2. Contact Reasons: Relative FTE Change 2018-2019

```{r, include = TRUE}
t_call_times %>%
  # Transform data
  filter(PRODUCT_LINE != "UNKNOWN") %>%
  filter(
    (EVENT_END >= as.Date("2018-01-01") & EVENT_END < as.Date("2018-06-01")) |
      (EVENT_END >= as.Date("2019-01-01") & EVENT_END < as.Date("2019-06-01"))
  ) %>%
  mutate(YEAR = forcats::fct_rev(factor(as.character(lubridate::year(EVENT_END))))) %>%
  mutate(
    EVENT_MONTH = floor_date(EVENT_END, unit = "month"),
    SEGMENT = forcats::fct_rev(forcats::fct_lump(paste(CASE_TYPE_EN, PRODUCT_LINE), n = 9, other_level = "Everything else"))
  ) %>%
  filter(SEGMENT != "Everything else") %>%
  group_by(YEAR, EVENT_MONTH, SEGMENT) %>%
  summarize(
    CALL_VOLUME = n(),
    CALL_TIME_SEC = sum(CALL_TIME)
  ) %>%
  ungroup() %>%
  left_join(t_mnap, by = c("EVENT_MONTH" = "IDOSZAK")) %>%
  mutate(FTE = CALL_TIME_SEC/ 60/ 60/ 7/ MNAP) %>% 
  group_by(YEAR, SEGMENT) %>% 
  summarize(FTE = mean(FTE)) %>% 
  ungroup() %>% 
  group_by(YEAR) %>% 
  mutate(FTE_PCT = FTE/sum(FTE)) %>% 
  ungroup() %>% 
  ggplot(aes(x = SEGMENT, FTE_PCT, fill = YEAR)) +
    geom_bar(stat = "identity", position = position_dodge()) +
    geom_text(aes(label = paste(round(FTE_PCT*100, 2), "%")), position = position_dodge(width = 1), size = 3) +
    scale_y_continuous(labels = percent) +
    coord_flip() +
    guides(fill = guide_legend(reverse = TRUE)) +
    labs(
      x = "Contact Reason",
      y = "% of total FTE",
      title = "Relative FTE Change 2018-2019"
    )
```

***


# 3. Root-Cause Analysis

## 3.1. Call Types FTE

The FTE of each process can be broken by call type. Call type is the service or solution provided for the customer in the call.

Note the other category can broken down for further call types if neccessary.

```{r, fig.width=10}
t_call_times %>%
  # Transform data
  filter(PRODUCT_LINE != "UNKNOWN") %>%
  filter(
    (EVENT_END >= as.Date('2018-01-01') & EVENT_END < as.Date('2018-06-01')) |
    (EVENT_END >= as.Date('2019-01-01') & EVENT_END < as.Date('2019-06-01'))
         ) %>%
  mutate(YEAR = lubridate::year(EVENT_END)) %>% 
  mutate(EVENT_MONTH = floor_date(EVENT_END, unit = "month"),
         #CASE_TYPE_EN = forcats::fct_lump(factor(CASE_TYPE_EN), n = 7),
         SEGMENT = forcats::fct_lump(paste(CASE_TYPE_EN, PRODUCT_LINE), n = 13)) %>%
  mutate(ACTIVITY_EN = case_when(ACTIVITY_EN == "Premium settlement" ~ "Provide information Premium settlement",
                                 TRUE ~ ACTIVITY_EN)) %>% 
  group_by(YEAR, EVENT_MONTH, SEGMENT) %>% 
  mutate(ACTIVITY_EN = as.character(forcats::fct_lump(ACTIVITY_EN, prop = 0.05))) %>% 
  ungroup() %>% 
  group_by(YEAR, EVENT_MONTH, SEGMENT, ACTIVITY_EN) %>%
  summarize(CALL_VOLUME = n(),
            CALL_TIME_SEC = sum(CALL_TIME)) %>%
  ungroup() %>%
  left_join(t_mnap, by = c("EVENT_MONTH" = "IDOSZAK")) %>% 
  mutate(FTE = CALL_TIME_SEC/60/60/7/MNAP,
         COST = FTE/CALL_VOLUME*1000) %>%
  # Compute monthly averages
  group_by(YEAR, SEGMENT, ACTIVITY_EN) %>% 
  summarize(
            CALL_VOLUME = mean(CALL_VOLUME),
            FTE = mean(FTE),
            COST = mean(COST)) %>%
  ungroup() %>% 
  filter(SEGMENT %in% c('Claim report HOUSE', 'Claim report CAR', 'Provide information CAR', 'Provide information HOUSE')) %>% 
  select(YEAR, SEGMENT, ACTIVITY_EN, FTE) %>% 
  mutate(SEGMENT = forcats::fct_relevel(SEGMENT, 'Claim report HOUSE', 'Claim report CAR',
                                        'Provide information CAR', 'Provide information HOUSE')) %>%
  mutate(ACTIVITY_EN = forcats::fct_reorder(ACTIVITY_EN, FTE, sum)) %>% 
  mutate(ACTIVITY_EN = forcats::fct_relevel(ACTIVITY_EN, "Other")) %>%
  # Plot
  ggplot(aes(x = ACTIVITY_EN, y = FTE)) +
    geom_bar(stat = "identity") +
    theme(strip.text.y = element_text(angle=0)) +
    coord_flip() +
    facet_grid(YEAR~SEGMENT, labeller = label_wrap_gen(width=10)) +
    labs(
      x = "Call types",
    y = "FTE",
    title = "Call Types: FTE Comparison 2018-2019"
    )
```


### 3.1.2. Call Types: Absolute FTE Change 2018-2019

```{r, fig.width=10}
t_call_times %>%
  # Transform data
  filter(PRODUCT_LINE != "UNKNOWN") %>%
  filter(
    (EVENT_END >= as.Date('2018-01-01') & EVENT_END < as.Date('2018-06-01')) |
    (EVENT_END >= as.Date('2019-01-01') & EVENT_END < as.Date('2019-06-01'))
         ) %>%
  mutate(YEAR = lubridate::year(EVENT_END)) %>% 
  mutate(EVENT_MONTH = floor_date(EVENT_END, unit = "month"),
         #CASE_TYPE_EN = forcats::fct_lump(factor(CASE_TYPE_EN), n = 7),
         SEGMENT = forcats::fct_lump(paste(CASE_TYPE_EN, PRODUCT_LINE), n = 13)) %>%
  mutate(ACTIVITY_EN = case_when(ACTIVITY_EN == "Premium settlement" ~ "Provide information Premium settlement",
                                 TRUE ~ ACTIVITY_EN)) %>% 
  group_by(YEAR, EVENT_MONTH, SEGMENT) %>% 
  mutate(ACTIVITY_EN = as.character(forcats::fct_lump(ACTIVITY_EN, prop = 0.05))) %>% 
  ungroup() %>% 
  group_by(YEAR, EVENT_MONTH, SEGMENT, ACTIVITY_EN) %>%
  summarize(CALL_VOLUME = n(),
            CALL_TIME_SEC = sum(CALL_TIME)) %>%
  ungroup() %>%
  left_join(t_mnap, by = c("EVENT_MONTH" = "IDOSZAK")) %>% 
  mutate(FTE = CALL_TIME_SEC/60/60/7/MNAP,
         COST = FTE/CALL_VOLUME*1000) %>%
  # Compute monthly averages
  group_by(YEAR, SEGMENT, ACTIVITY_EN) %>% 
  summarize(
            CALL_VOLUME = mean(CALL_VOLUME),
            FTE = mean(FTE),
            COST = mean(COST)) %>%
  ungroup() %>% 
  filter(SEGMENT %in% c('Claim report HOUSE', 'Claim report CAR', 'Provide information CAR', 'Provide information HOUSE')) %>% 
  select(YEAR, SEGMENT, ACTIVITY_EN, FTE) %>% 
  mutate(SEGMENT = forcats::fct_relevel(SEGMENT, 'Claim report HOUSE', 'Claim report CAR',
                                        'Provide information CAR', 'Provide information HOUSE')) %>%
  mutate(ACTIVITY_EN = forcats::fct_reorder(ACTIVITY_EN, FTE, sum)) %>% 
  mutate(ACTIVITY_EN = forcats::fct_relevel(ACTIVITY_EN, "Other")) %>%
  myspread(YEAR, FTE) %>%
  filter(complete.cases(.)) %>% 
  mutate(FTE = FTE_2019/FTE_2018 -1) %>% 
  # Plot
  ggplot(aes(x = ACTIVITY_EN, y = FTE)) +
    geom_bar(aes(fill = FTE < 0), stat = "identity") +
    scale_fill_manual(guide = FALSE, breaks = c(TRUE, FALSE), values = c("#FF6347", "#90EE90")) +
    scale_y_continuous(labels = percent) +
    theme(strip.text.y = element_text(angle=0)) +
    geom_hline(yintercept = 0, colour = "#A9A9A9", linetype = "longdash") +
    coord_flip(ylim = c(-0.5, 0.5)) +
    facet_grid(.~SEGMENT, labeller = label_wrap_gen(width=10)) +
    labs(
      x = "Call types",
    y = "FTE Absolute Change Rate (%)",
    title = "Call Types: Absolute FTE Change 2018-2019"
    )
```



### 3.1.3. Call Types: Relative FTE Change 2018-2019

```{r, fig.width=10}
t_call_times %>%
  # Transform data
  filter(PRODUCT_LINE != "UNKNOWN") %>%
  filter(
    (EVENT_END >= as.Date('2018-01-01') & EVENT_END < as.Date('2018-06-01')) |
    (EVENT_END >= as.Date('2019-01-01') & EVENT_END < as.Date('2019-06-01'))
         ) %>%
  mutate(YEAR = forcats::fct_rev(factor(as.character(lubridate::year(EVENT_END))))) %>%
  mutate(EVENT_MONTH = floor_date(EVENT_END, unit = "month"),
         #CASE_TYPE_EN = forcats::fct_lump(factor(CASE_TYPE_EN), n = 7),
         SEGMENT = forcats::fct_lump(paste(CASE_TYPE_EN, PRODUCT_LINE), n = 13)) %>%
  mutate(ACTIVITY_EN = case_when(ACTIVITY_EN == "Premium settlement" ~ "Provide information Premium settlement",
                                 TRUE ~ ACTIVITY_EN)) %>% 
  group_by(YEAR, EVENT_MONTH, SEGMENT) %>% 
  mutate(ACTIVITY_EN = as.character(forcats::fct_lump(ACTIVITY_EN, prop = 0.05))) %>% 
  ungroup() %>% 
  group_by(YEAR, EVENT_MONTH, SEGMENT, ACTIVITY_EN) %>%
  summarize(CALL_VOLUME = n(),
            CALL_TIME_SEC = sum(CALL_TIME)) %>%
  ungroup() %>%
  left_join(t_mnap, by = c("EVENT_MONTH" = "IDOSZAK")) %>% 
  mutate(FTE = CALL_TIME_SEC/60/60/7/MNAP,
         COST = FTE/CALL_VOLUME*1000) %>%
  # Compute monthly averages
  group_by(YEAR, SEGMENT, ACTIVITY_EN) %>% 
  summarize(
            CALL_VOLUME = mean(CALL_VOLUME),
            FTE = mean(FTE),
            COST = mean(COST)) %>%
  ungroup() %>% 
  group_by(YEAR, SEGMENT) %>% 
  mutate(FTE_PCT = FTE/sum(FTE)) %>% 
  ungroup() %>% 
  filter(SEGMENT %in% c('Claim report HOUSE', 'Claim report CAR', 'Provide information CAR', 'Provide information HOUSE')) %>% 
  select(YEAR, SEGMENT, ACTIVITY_EN, FTE_PCT) %>% 
  mutate(SEGMENT = forcats::fct_relevel(SEGMENT, 'Claim report HOUSE', 'Claim report CAR',
                                        'Provide information CAR', 'Provide information HOUSE')) %>%
  mutate(ACTIVITY_EN = forcats::fct_reorder(ACTIVITY_EN, FTE_PCT, sum)) %>% 
  mutate(ACTIVITY_EN = forcats::fct_relevel(ACTIVITY_EN, "Other")) %>%
  # Plot
  ggplot(aes(x = ACTIVITY_EN, y = FTE_PCT, fill = YEAR)) +
    geom_bar(stat = "identity", position=position_dodge()) +
    geom_text(aes(label = paste(round(FTE_PCT*100, 2), "%")), position = position_dodge(width = 1), size = 3) +
    scale_y_continuous(labels = percent, breaks = c(0, 0.2, 0.4)) +
    coord_flip() +
    guides(fill = guide_legend(reverse = TRUE)) +
    facet_grid(.~SEGMENT, labeller = label_wrap_gen(width=10)) +
    labs(
      x = "Call types",
    y = "% of total FTE",
    title = "Relative FTE Change 2018-2019"
    )
```



## 3.2. Wrap-Up Analysis

Total FTE can be broken down to  

* speak-time FTE
* wrap-up FTE

> In 2019 31% of FTE is spent on wrap-ups. That is a 10% increase compared to 2018

```{r}
t_call_times %>%
  # Transform data
  filter(PRODUCT_LINE != "UNKNOWN") %>% 
  filter(
    (EVENT_END >= as.Date('2018-01-01') & EVENT_END < as.Date('2018-06-01')) |
    (EVENT_END >= as.Date('2019-01-01') & EVENT_END < as.Date('2019-06-01'))
         ) %>%
  mutate(YEAR = lubridate::year(EVENT_END)) %>% 
  mutate(EVENT_MONTH = floor_date(EVENT_END, unit = "month")) %>%
  group_by(YEAR, EVENT_MONTH) %>%
  summarize(
        CALL_VOLUME = n(),
        CALL_TIME_SEC = sum(CALL_TIME),
        SPEAK_TIME_SEC = sum(SPEAK_TIME),
        WRAPUP_TIME_SEC = sum(WRAPUP_TIME)) %>%
  ungroup() %>%
  left_join(t_mnap, by = c("EVENT_MONTH" = "IDOSZAK")) %>% 
  mutate(
    FTE = CALL_TIME_SEC/60/60/7/MNAP,
    COST = FTE/CALL_VOLUME*1000,
    SPEAK_FTE = SPEAK_TIME_SEC/60/60/7/MNAP,
    SPEAK_COST = SPEAK_FTE/CALL_VOLUME*1000,
    WRAPUP_FTE = WRAPUP_TIME_SEC/60/60/7/MNAP,
    WRAPUP_COST = WRAPUP_FTE/CALL_VOLUME*1000) %>%
  # Compute monthly averages
  group_by(YEAR) %>% 
  summarize(
            CALL_VOLUME = mean(CALL_VOLUME),
            FTE = mean(FTE),
            COST = mean(COST),
            SPEAK_FTE = mean(SPEAK_FTE),
            SPEAK_COST = mean(SPEAK_COST),
            WRAPUP_FTE = mean(WRAPUP_FTE),
            WRAPUP_COST = mean(WRAPUP_COST)) %>% 
  ungroup() %>% 
  mutate(WRAPUP_RATIO = WRAPUP_FTE/FTE) %>% 
  # Plot
  ggplot(aes(x = as.character(YEAR), y = WRAPUP_RATIO)) +
    geom_bar(stat = "identity") +
    geom_text(aes(label = paste(round(WRAPUP_RATIO*100), "%")), vjust = -0.1) +
    scale_y_continuous(label = percent) +
    #facet_grid(YEAR~.) +
    labs(
      x = "Year",
    y = "Ratio of Wrap-up FTE to Total FTE",
    title = "Proprotion of FTE Spent on Wrap-up"
    )
```

### 3.2.1. Wrap-Up FTE Ratio by Request Type

```{r}
t_call_times %>%
  # Transform data
  filter(PRODUCT_LINE != "UNKNOWN") %>% 
  filter(
    (EVENT_END >= as.Date('2018-01-01') & EVENT_END < as.Date('2018-06-01')) |
    (EVENT_END >= as.Date('2019-01-01') & EVENT_END < as.Date('2019-06-01'))
         ) %>%
  mutate(YEAR = lubridate::year(EVENT_END)) %>% 
  mutate(EVENT_MONTH = floor_date(EVENT_END, unit = "month"),
         #CASE_TYPE_EN = forcats::fct_lump(factor(CASE_TYPE_EN), n = 7),
         SEGMENT = forcats::fct_lump(paste(CASE_TYPE_EN, PRODUCT_LINE), n = 9, other_level = "Everything else")) %>%
  group_by(YEAR, EVENT_MONTH,  SEGMENT) %>%
  summarize(
        CALL_VOLUME = n(),
        CALL_TIME_SEC = sum(CALL_TIME),
        SPEAK_TIME_SEC = sum(SPEAK_TIME),
        WRAPUP_TIME_SEC = sum(WRAPUP_TIME)) %>%
  ungroup() %>%
  left_join(t_mnap, by = c("EVENT_MONTH" = "IDOSZAK")) %>% 
  mutate(
    FTE = CALL_TIME_SEC/60/60/7/MNAP,
    COST = FTE/CALL_VOLUME*1000,
    SPEAK_FTE = SPEAK_TIME_SEC/60/60/7/MNAP,
    SPEAK_COST = SPEAK_FTE/CALL_VOLUME*1000,
    WRAPUP_FTE = WRAPUP_TIME_SEC/60/60/7/MNAP,
    WRAPUP_COST = WRAPUP_FTE/CALL_VOLUME*1000) %>%
  # Compute monthly averages
  group_by(YEAR, SEGMENT) %>% 
  summarize(
            CALL_VOLUME = mean(CALL_VOLUME),
            FTE = mean(FTE),
            COST = mean(COST),
            SPEAK_FTE = mean(SPEAK_FTE),
            SPEAK_COST = mean(SPEAK_COST),
            WRAPUP_FTE = mean(WRAPUP_FTE),
            WRAPUP_COST = mean(WRAPUP_COST)) %>% 
  ungroup() %>% 
  mutate(WRAPUP_RATIO = WRAPUP_FTE/FTE) %>% 
  mutate(SEGMENT = forcats::fct_reorder(SEGMENT, WRAPUP_RATIO, sum)) %>% 
  mutate(SEGMENT = forcats::fct_relevel(SEGMENT, "Everything else")) %>% 
  # Plot
  ggplot(aes(x = SEGMENT, y = WRAPUP_RATIO)) +
    geom_bar(stat = "identity") +
    scale_y_continuous(label = percent) +
    coord_flip() +
    facet_grid(YEAR~.) +
    labs(
      x = "Request Type",
    y = "Ratio of Wrap-up FTE to Total FTE",
    title = "Proprotion of FTE Spent on Wrap-up"
    )
```

### 3.2.2. Wrap-Up FTE Ratio Change 2018-2019

```{r}
t_call_times %>%
  # Transform data
  filter(PRODUCT_LINE != "UNKNOWN") %>% 
  filter(
    (EVENT_END >= as.Date('2018-01-01') & EVENT_END < as.Date('2018-06-01')) |
    (EVENT_END >= as.Date('2019-01-01') & EVENT_END < as.Date('2019-06-01'))
         ) %>%
  mutate(YEAR = lubridate::year(EVENT_END)) %>% 
  mutate(EVENT_MONTH = floor_date(EVENT_END, unit = "month"),
         #CASE_TYPE_EN = forcats::fct_lump(factor(CASE_TYPE_EN), n = 7),
         SEGMENT = forcats::fct_lump(paste(CASE_TYPE_EN, PRODUCT_LINE), n = 9, other_level = "Everything else")) %>%
  filter(SEGMENT != "Everything else") %>%
  group_by(YEAR, EVENT_MONTH,  SEGMENT) %>%
  summarize(
        CALL_VOLUME = n(),
        CALL_TIME_SEC = sum(CALL_TIME),
        SPEAK_TIME_SEC = sum(SPEAK_TIME),
        WRAPUP_TIME_SEC = sum(WRAPUP_TIME)) %>%
  ungroup() %>%
  left_join(t_mnap, by = c("EVENT_MONTH" = "IDOSZAK")) %>% 
  mutate(
    FTE = CALL_TIME_SEC/60/60/7/MNAP,
    COST = FTE/CALL_VOLUME*1000,
    SPEAK_FTE = SPEAK_TIME_SEC/60/60/7/MNAP,
    SPEAK_COST = SPEAK_FTE/CALL_VOLUME*1000,
    WRAPUP_FTE = WRAPUP_TIME_SEC/60/60/7/MNAP,
    WRAPUP_COST = WRAPUP_FTE/CALL_VOLUME*1000) %>%
  # Compute monthly averages
  group_by(YEAR, SEGMENT) %>% 
  summarize(
            CALL_VOLUME = mean(CALL_VOLUME),
            FTE = mean(FTE),
            COST = mean(COST),
            SPEAK_FTE = mean(SPEAK_FTE),
            SPEAK_COST = mean(SPEAK_COST),
            WRAPUP_FTE = mean(WRAPUP_FTE),
            WRAPUP_COST = mean(WRAPUP_COST)) %>% 
  ungroup() %>% 
  mutate(WRAPUP_RATIO = WRAPUP_FTE/FTE) %>% 
  select(YEAR, SEGMENT, WRAPUP_RATIO) %>% 
  mutate(SEGMENT = forcats::fct_rev(SEGMENT)) %>% 
  #mutate(SEGMENT = forcats::fct_reorder(SEGMENT, WRAPUP_RATIO, sum)) %>% 
  #mutate(SEGMENT = forcats::fct_relevel(SEGMENT, "Everything else")) %>% 
  myspread(YEAR, WRAPUP_RATIO) %>% 
  mutate(WRAPUP = WRAPUP_RATIO_2019/WRAPUP_RATIO_2018 - 1) %>% 
  # Plot
  ggplot(aes(x = SEGMENT, y = WRAPUP)) +
    geom_bar(aes(fill = WRAPUP < 0), stat = "identity") +
    scale_fill_manual(guide = FALSE, breaks = c(TRUE, FALSE), values = c("#FF6347", "#90EE90")) +
    scale_y_continuous(labels = percent) +
    geom_hline(yintercept = 0, colour = "#A9A9A9", linetype = "longdash") +
    coord_flip(ylim = c(-0.25, 0.25)) +
    labs(
      x = "Contact Reason",
    y = "Rate of Change (%)",
    title = "Change of Wrap-up FTE Ratio 2018-2019"
    )
```


## 3.3. Calls per Request

### 3.3.1 Calls per Request by Request Type

```{r}
t_call_times %>%
  # Transform data
  filter(PRODUCT_LINE != "UNKNOWN") %>% 
   filter(
    (EVENT_END >= as.Date('2018-01-01') & EVENT_END < as.Date('2018-06-01')) |
    (EVENT_END >= as.Date('2019-01-01') & EVENT_END < as.Date('2019-06-01'))
         ) %>%
  mutate(YEAR = lubridate::year(EVENT_END)) %>% 
  mutate(EVENT_MONTH = floor_date(EVENT_END, unit = "month"),
         #CASE_TYPE_EN = forcats::fct_lump(factor(CASE_TYPE_EN), n = 7),
         SEGMENT = forcats::fct_lump(paste(CASE_TYPE_EN, PRODUCT_LINE), n = 13, other_level = "Everything else")) %>%
  group_by(YEAR, EVENT_MONTH,  SEGMENT, CASE_ID) %>%
  summarize(
        CALL_VOLUME = n()) %>%
  ungroup() %>%
  group_by(YEAR, SEGMENT) %>% 
  summarize(CALL_PER_REQUEST = mean(CALL_VOLUME)) %>% 
  ungroup() %>% 
  mutate(SEGMENT = forcats::fct_reorder(SEGMENT, CALL_PER_REQUEST, sum)) %>% 
  mutate(SEGMENT = forcats::fct_relevel(SEGMENT, "Everything else")) %>% 
  # Plot
  ggplot(aes(x = SEGMENT, y = CALL_PER_REQUEST)) +
    geom_bar(stat = "identity") +
    coord_flip(ylim = c(1, 1.5)) +
    facet_grid(YEAR~.) +
    labs(
      x = "Request Type",
    y = "Calls per Request",
    title = "Average Number of Calls on a Single Request"
    )
```


### 3.3.2. Calls per Request Change 2018-2019

```{r}
t_call_times %>%
  # Transform data
  filter(PRODUCT_LINE != "UNKNOWN") %>% 
   filter(
    (EVENT_END >= as.Date('2018-01-01') & EVENT_END < as.Date('2018-06-01')) |
    (EVENT_END >= as.Date('2019-01-01') & EVENT_END < as.Date('2019-06-01'))
         ) %>%
  mutate(YEAR = lubridate::year(EVENT_END)) %>% 
  mutate(EVENT_MONTH = floor_date(EVENT_END, unit = "month"),
         #CASE_TYPE_EN = forcats::fct_lump(factor(CASE_TYPE_EN), n = 7),
         SEGMENT = forcats::fct_lump(paste(CASE_TYPE_EN, PRODUCT_LINE), n = 13, other_level = "Everything else")) %>%
  group_by(YEAR, EVENT_MONTH,  SEGMENT, CASE_ID) %>%
  summarize(
        CALL_VOLUME = n()) %>%
  ungroup() %>%
  group_by(YEAR, SEGMENT) %>% 
  summarize(CALL_PER_REQUEST = mean(CALL_VOLUME)) %>% 
  ungroup() %>% 
  mutate(SEGMENT = forcats::fct_reorder(SEGMENT, CALL_PER_REQUEST, sum)) %>% 
  mutate(SEGMENT = forcats::fct_relevel(SEGMENT, "Everything else")) %>% 
  myspread(YEAR, CALL_PER_REQUEST) %>% 
  mutate(CALL_PER_REQUEST = CALL_PER_REQUEST_2019/CALL_PER_REQUEST_2018 - 1) %>% 
  # Plot
  ggplot(aes(x = SEGMENT, y = CALL_PER_REQUEST)) +
    geom_bar(aes(fill = CALL_PER_REQUEST < 0), stat = "identity") +
    scale_fill_manual(guide = FALSE, breaks = c(TRUE, FALSE), values = c("#FF6347", "#90EE90")) +
    scale_y_continuous(labels = percent) +
    geom_hline(yintercept = 0, colour = "#A9A9A9", linetype = "longdash") +
    coord_flip(ylim = c(-0.10, 0.10)) +
    labs(
      x = "Rate of Change (%)",
    y = "Ratio of Wrap-up FTE to Total FTE (in decreasing order of absolute num of calls per request)",
    title = "Change of Calls per Request 2018-2019"
    )
```


### 3.3.3. Queries to Requests

```{r, include = TRUE}
t_call_times %>%
  # Transform data
  filter(PRODUCT_LINE != "UNKNOWN") %>% 
  filter(
    (EVENT_END >= as.Date('2018-01-01') & EVENT_END < as.Date('2018-06-01')) |
    (EVENT_END >= as.Date('2019-01-01') & EVENT_END < as.Date('2019-06-01'))
         ) %>%
  mutate(YEAR = paste("Jan-May", lubridate::year(EVENT_END))) %>% 
  mutate(EVENT_MONTH = floor_date(EVENT_END, unit = "month"),
         #CASE_TYPE_EN = forcats::fct_lump(factor(CASE_TYPE_EN), n = 7),
         SEGMENT = forcats::fct_lump(paste(CASE_TYPE_EN, PRODUCT_LINE), n = 9, other_level = "Everything else"),
         CONTACT_TYPE = case_when (stringr::str_detect(ACTIVITY_EN, "Provide information") ~ "Query",
         TRUE ~ "Request"))%>%
  group_by(YEAR, EVENT_MONTH, CONTACT_TYPE) %>%
  summarize(CALL_VOLUME = n(),
            CALL_TIME_SEC = sum(CALL_TIME)) %>%
  ungroup() %>%
  left_join(t_mnap, by = c("EVENT_MONTH" = "IDOSZAK")) %>% 
  mutate(FTE = CALL_TIME_SEC/60/60/7/MNAP,
         COST = FTE/CALL_VOLUME*1000) %>%
  # Compute monthly averages
  group_by(YEAR, CONTACT_TYPE) %>% 
  summarize(
            CALL_VOLUME = mean(CALL_VOLUME),
            FTE = mean(FTE),
            COST = mean(COST)) %>%
  ungroup() %>%
  tidyr::gather(key = METRIC, value = VALUE, -YEAR, -CONTACT_TYPE) %>%
  filter(METRIC != "COST") %>% 
  # Plot
 ggplot(aes(x = CONTACT_TYPE, y = VALUE, fill = YEAR)) +
    geom_bar(stat = "identity", position=position_dodge()) +
    facet_grid(METRIC~., scales = "free") +
    labs(
      x = "Contact type",
    y = "",
    title = "Query v Request 2018-2019"
    )
```