---
title: "Contact Center: Top 3 Requests Overview"
author: "János Poór"
date: 'May 17, 2019'
output: rmdformats::readthedown
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, message=FALSE, warning=FALSE}
library(here)
library(dplyr)
library(ggplot2)
library(lubridate)
library(scales)
library(tidyr)
library(ggrepel)
library(forcats)
```

```{r, message=FALSE}
t_ccc_pa <- read.csv(here::here("Data" ,"t_ccc_pa_local_export_top3.csv"), sep = ";", stringsAsFactors = FALSE)
t_mnap <- read.csv(here::here("Data" ,"t_mnap.csv"), sep = ";", stringsAsFactors = FALSE)

# Transform Data Types Inplace
t_ccc_pa <- t_ccc_pa %>%
  mutate(EVENT_END = ymd_hms(EVENT_END)) %>% 
  filter(EVENT_END < as.Date('2019-01-01'))

t_mnap <- t_mnap %>% mutate(IDOSZAK = ymd_hms(IDOSZAK))

t_ccc_pa[t_ccc_pa$CASE_TYPE_EN == "Delete contract", "CASE_TYPE_EN"] <- "Contract termination"

t_ccc_pa[t_ccc_pa$CASE_TYPE_EN == "Claim report" &
  t_ccc_pa$ACTIVITY_EN %in% c("Provide information Property assignments", "Provide information Motor vehicle claim report", "Provide information") &
  startsWith(t_ccc_pa$CASE_ID, "S"), "ACTIVITY_EN"] <- "Provide information claim related"

t_ccc_pa[t_ccc_pa$CASE_TYPE_EN == "Claim report" &
  t_ccc_pa$ACTIVITY_EN %in% c("Provide information Property assignments", "Provide information Motor vehicle claim report", "Provide information") &
  startsWith(t_ccc_pa$CASE_ID, "K"), "ACTIVITY_EN"] <- "Provide information on claim file"
```

# 1. Introduction and Glossary

The last expert session defined three major request types of interest: 

* Claim report
* Contract termination
* Provide information

> This analysis provides insights into the basic structure of the Contact Center interactions across the three major request types.

Glossary of terms:  

* Request (case): a single customer request that might have been answered via more than one Contact Center interaction
* Interaction: a single Contact Center interaction (single touch on request) that may be of different channels (call, e-mail, public internet etc.)

As of now exact interaction durations can only computed for calls that are analysed in a separate document (Call Center: Call Times and FTE)


# 2. Identify the Biggest Volumes

## 2.1. Number of Requests and Interactions by Month

Biggest interaction volumes in:  

* HOUSE claim report
* CAR contract termination


```{r}
t_ccc_pa %>%
  # Transform data
  filter(PRODUCT_LINE != "UNKNOWN") %>% 
  mutate(EVENT_MONTH = floor_date(EVENT_END, unit = "month")) %>%
  group_by(CASE_ID, CASE_TYPE_EN, PRODUCT_LINE) %>%
  mutate(CASE_START_MONTH = min(EVENT_MONTH)) %>%
  ungroup() %>%
  group_by(CASE_START_MONTH, CASE_TYPE_EN, PRODUCT_LINE) %>%
  summarize(Requests = n_distinct(CASE_ID),
            Interactions = n()) %>%
  ungroup() %>%
  mutate(EVENT_PER_CASE = Interactions/Requests) %>% 
  # Plot
  ggplot(aes(x = substr(as.character(CASE_START_MONTH), 1, 7), group = 1)) +
  geom_line(aes(y = Requests, colour = "Requests"), size = 0.8) +
  geom_line(aes(y = Interactions, colour = "Interactions"), size = 0.8) +
  scale_y_continuous(label = unit_format(unit = "K", scale = 1e-3)) +
  theme(axis.text.x = element_text(angle = 90, size = 6)) +
  facet_grid(CASE_TYPE_EN~PRODUCT_LINE, labeller = label_wrap_gen(width=10)) +
  labs(
    x = "Month",
    y = "Count",
    title = "Number of Requests (Cases) and Interactions (Events) per Month"
  )
```

## 2.2. Number of Interactions per a Single Request

Requests handled by most interactions are:

* CAR claim reports
* LIFE contract terminations

> Note: sheer interaction counts do not necessarily coincide with highest FTE consumption. FTE cosuption patterns are different for calls where exact FTE measures are availble (for further details see Call Center: Call Times and FTE analysis)

```{r}
t_ccc_pa %>%
  # Transform data
  filter(PRODUCT_LINE != "UNKNOWN") %>% 
  mutate(EVENT_MONTH = floor_date(EVENT_END, unit = "month")) %>%
  group_by(CASE_ID, CASE_TYPE_EN, PRODUCT_LINE) %>%
  mutate(CASE_START_MONTH = min(EVENT_MONTH)) %>%
  ungroup() %>%
  group_by(CASE_START_MONTH, CASE_TYPE_EN, PRODUCT_LINE) %>%
  summarize(CASES = n_distinct(CASE_ID),
            EVENTS = n()) %>%
  ungroup() %>%
  mutate(EVENT_PER_CASE = EVENTS/CASES) %>% 
  # Plot
  ggplot(aes(x = substr(as.character(CASE_START_MONTH), 1, 7), group = 1)) +
  geom_line(aes(y = EVENT_PER_CASE), size = 0.8) +
  theme(axis.text.x = element_text(angle = 90, size = 6)) +
  facet_grid(CASE_TYPE_EN~PRODUCT_LINE, labeller = label_wrap_gen(width=10)) +
  labs(
    x = "Month",
    y = "Count",
    title = "Number of Interactions per Request"
  )
```


## 2.3. Channel Map of Request Types

```{r}
t_ccc_pa %>%
  # Transform data
  filter(PRODUCT_LINE != "UNKNOWN") %>% 
  mutate(EVENT_MONTH = floor_date(EVENT_END, unit = "month")) %>%
  group_by(CASE_ID, CASE_TYPE_EN, PRODUCT_LINE, EVENT_CHANNEL) %>%
  mutate(CASE_START_MONTH = min(EVENT_MONTH)) %>%
  ungroup() %>%
  group_by(CASE_START_MONTH, CASE_TYPE_EN, PRODUCT_LINE, EVENT_CHANNEL) %>%
  summarize(CASES = n_distinct(CASE_ID),
            EVENTS = n()) %>%
  ungroup() %>%
  mutate(EVENT_PER_CASE = EVENTS/CASES,
         SEGMENT = paste(PRODUCT_LINE, CASE_TYPE_EN)) %>%
  group_by(PRODUCT_LINE, CASE_TYPE_EN, SEGMENT, EVENT_CHANNEL) %>%
  summarize(CASES = mean(CASES),
            EVENTS = mean(EVENTS),
            EVENTS_PER_CASE = mean(EVENT_PER_CASE)) %>% 
  ungroup() %>% 
  # Plot
  ggplot(aes(x = EVENT_CHANNEL, y = EVENTS)) +
    geom_bar(stat = "identity") +
    theme(axis.text.x = element_text(angle = 90)) +
    #scale_y_continuous(label = unit_format(unit = "K", scale = 1e-3)) +
    coord_flip() +
    facet_grid(CASE_TYPE_EN ~ PRODUCT_LINE, labeller = label_wrap_gen(width=10)) +
    labs(
      x = "Channel",
    y = "Interactions (Monthly Average)",
    title = "Channel Map of Major Request Types"
    )
```

***

# 3. Understanding Interactions

## 3.1. Major Interaction Types

Interactions can be broked down by type. Interaction type is the service or solution provided for the customer in the call.

The graph provides two insights:  

* High volume of the "Other" is due to the large number of wrap-up tree leaves operators can log onto the interaction. The large number of available options result in many small fequency categories that are put into the "Other" category
* The interaction type with the highest frequency is the "Internal traffic activity" that combines all internal, logistic activities done on the request. These interactions do not give direct value to the customer, but are the result of the manual toggling of the workflow.

```{r}
t_ccc_pa %>%
  # Transform data
  filter(PRODUCT_LINE != "UNKNOWN") %>%
  mutate(
    EVENT_MONTH = floor_date(EVENT_END, unit = "month"),
    ACTIVITY_EN = case_when(
    ACTIVITY_EN %in% c("Transmission", "Forward activity") ~ "Internal traffic activity",
    TRUE ~ ACTIVITY_EN
  )) %>%
  mutate(ACTIVITY_EN = forcats::fct_lump(factor(ACTIVITY_EN), n = 20)) %>%
  group_by(ACTIVITY_EN, EVENT_MONTH) %>% 
  summarize(COUNT = n()) %>% 
  ungroup() %>% 
  group_by(ACTIVITY_EN) %>% 
  summarize(COUNT = mean(COUNT)) %>% 
  ungroup() %>% 
  mutate(ACTIVITY_EN = forcats::fct_reorder(ACTIVITY_EN, COUNT, sum)) %>% 
  mutate(ACTIVITY_EN = forcats::fct_relevel(ACTIVITY_EN, "Other", "Internal traffic activity")) %>% 
  # Plor
  #ggplot(aes(x = factor(ACTIVITY_EN, levels = unique(ACTIVITY_EN[order(COUNT)])), y = COUNT)) +
  ggplot(aes(x =ACTIVITY_EN, y = COUNT)) +
    geom_bar(stat = "identity") +
    scale_y_continuous(label = unit_format(unit = "K", scale = 1e-3)) +
    coord_flip() +
    labs(
      x = "Activity",
      y = "# of Interactions (Monthly Average)",
      title = "Major Interaction Types"
    )
```

## 3.2. Interaction Types by Channel

```{r}
t_ccc_pa %>%
  # Transform data
  filter(PRODUCT_LINE != "UNKNOWN") %>%
  mutate(
    EVENT_MONTH = floor_date(EVENT_END, unit = "month"),
    ACTIVITY_EN = case_when(
    ACTIVITY_EN %in% c("Transmission", "Forward activity") ~ "Internal traffic activity",
    TRUE ~ ACTIVITY_EN
  )) %>%
  mutate(ACTIVITY_EN = forcats::fct_lump(factor(ACTIVITY_EN), n = 12)) %>%
  group_by(EVENT_CHANNEL, ACTIVITY_EN, EVENT_MONTH) %>% 
  summarize(COUNT = n()) %>% 
  ungroup() %>% 
  group_by(EVENT_CHANNEL, ACTIVITY_EN) %>% 
  summarize(COUNT = mean(COUNT)) %>% 
  ungroup() %>% 
  mutate(ACTIVITY_EN = forcats::fct_reorder(ACTIVITY_EN, COUNT, sum)) %>% 
  mutate(ACTIVITY_EN = forcats::fct_relevel(ACTIVITY_EN, "Other", "Internal traffic activity")) %>% 
  # Plor
  ggplot(aes(x = ACTIVITY_EN, y = COUNT)) +
    geom_bar(stat = "identity") +
    theme(axis.text.x = element_text(angle = 90)) +
    #scale_y_continuous(label = unit_format(unit = "K", scale = 1e-3)) +
    coord_flip() +
    facet_grid(.~EVENT_CHANNEL) +
    labs(
      x = "Interaction type",
      y = "# of Interactions (Monthly Average)",
      title = "Major Interaction Types by Channel"
    )
```

## 3.3. Interactions by Channel and Process

```{r, fig.width=14, fig.height=14}
t_ccc_pa %>%
  # Transform data
  filter(PRODUCT_LINE != "UNKNOWN") %>%
  mutate(
    SEGMENT = paste(PRODUCT_LINE, CASE_TYPE_EN),
    EVENT_MONTH = floor_date(EVENT_END, unit = "month"),
    ACTIVITY_EN = case_when(
    ACTIVITY_EN %in% c("Transmission", "Forward activity") ~ "Internal traffic activity",
    TRUE ~ ACTIVITY_EN
  )) %>%
  mutate(ACTIVITY_EN = forcats::fct_lump(factor(ACTIVITY_EN), n = 12)) %>%
  group_by(SEGMENT, EVENT_CHANNEL, ACTIVITY_EN, EVENT_MONTH) %>% 
  summarize(COUNT = n()) %>% 
  ungroup() %>% 
  group_by(SEGMENT, ACTIVITY_EN, EVENT_CHANNEL) %>% 
  summarize(COUNT = mean(COUNT)) %>% 
  ungroup() %>% 
  mutate(ACTIVITY_EN = forcats::fct_reorder(ACTIVITY_EN, COUNT, sum)) %>% 
  mutate(ACTIVITY_EN = forcats::fct_relevel(ACTIVITY_EN, "Other", "Internal traffic activity")) %>% 
  # Plor
  ggplot(aes(x = ACTIVITY_EN, y = COUNT)) +
    geom_bar(stat = "identity") +
    scale_y_continuous(label = unit_format(unit = "K", scale = 1e-3)) +
    coord_flip() +
    facet_grid(SEGMENT~EVENT_CHANNEL, labeller = label_wrap_gen(width=10)) +
    labs(
      x = "Interaction type",
      y = "# of Interactions (Monthly Average)",
      title = "Major Interaction Types"
    ) 
```


## 3.4. Interactions of Most Impactful Processes

```{r}
t_ccc_pa %>%
  # Transform data
  filter(PRODUCT_LINE != "UNKNOWN",
         EVENT_END >= as.Date('2018-01-01')) %>%
  mutate(
    SEGMENT = paste(CASE_TYPE_EN, PRODUCT_LINE),
    EVENT_MONTH = floor_date(EVENT_END, unit = "month"),
    ACTIVITY_EN = case_when(
    ACTIVITY_EN %in% c("Transmission", "Forward activity") ~ "Manual logistic",
    TRUE ~ "Value-adding"
  )) %>%
  filter(SEGMENT %in% c('Claim report HOUSE', 'Claim report CAR', 'Provide information CAR', 'Provide information HOUSE')) %>%
  filter(EVENT_CHANNEL != "CALL") %>% 
  group_by(SEGMENT, EVENT_MONTH, ACTIVITY_EN) %>% 
  summarize(COUNT = n(),
            COUNT_DISTINCT = n_distinct(CASE_ID)) %>% 
  ungroup() %>% 
  group_by(SEGMENT, ACTIVITY_EN) %>% 
  summarize(COUNT = mean(COUNT),
            COUNT_DISTINCT = mean(COUNT_DISTINCT)) %>% 
  ungroup() %>% 
  mutate(INT_PER_REQ = COUNT/COUNT_DISTINCT) %>% 
  mutate(SEGMENT = forcats::fct_relevel(SEGMENT, 'Claim report HOUSE', 'Claim report CAR',
                                        'Provide information CAR', 'Provide information HOUSE')) %>% 
  # Plor
  ggplot(aes(x = ACTIVITY_EN, y = COUNT)) +
    geom_bar(stat = "identity") +
    #scale_y_continuous(label = unit_format(unit = "K", scale = 1e-3)) +
    #coord_flip() +
    facet_grid(. ~ SEGMENT, labeller = label_wrap_gen(width=10)) +
     theme(axis.text.x = element_text(angle = 90)) +
    labs(
      x = "Interaction category",
      y = "# of Interactions (Monthly Average)",
      title = "Non-call Interactions"
    ) 
```