---
title: "Contact Center: Top 3 Requests Overview"
author: "János Poór"
date: 'May 9, 2019'
output: rmdformats::readthedown
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, message=FALSE, warning=FALSE}
library(here)
library(dplyr)
library(ggplot2)
library(lubridate)
library(scales)
library(tidyr)
library(ggrepel)
library(forcats)
```

```{r, message=FALSE}
t_ccc_pa <- read.csv(here::here("Data" ,"t_ccc_pa_local_export_top3.csv"), sep = ";", stringsAsFactors = FALSE)

# Transform Data Types Inplace
t_ccc_pa <- t_ccc_pa %>%
  mutate(EVENT_END = ymd_hms(EVENT_END)) %>% 
  filter(EVENT_END < as.Date('2019-01-01'))

t_ccc_pa[t_ccc_pa$CASE_TYPE_EN == "Delete contract", "CASE_TYPE_EN"] <- "Contract termination"
```

# Introduction

The Contact Center identified three major request types at the expert sessions on 5 March:  
* Claim report
* Contract termination
* Provide information

The Advanced Analytics Team delivers:
* Process maps further cleaned
* etc


# Identify the Biggest Impact

## Number of Cases by Month

Biggest volumes in
* CAR contract termination
* HOUSE claim report


```{r}
t_ccc_pa %>%
  # Transform data
  filter(PRODUCT_LINE != "UNKNOWN") %>% 
  mutate(EVENT_MONTH = floor_date(EVENT_END, unit = "month")) %>%
  group_by(CASE_ID, CASE_TYPE_EN, PRODUCT_LINE) %>%
  mutate(CASE_START_MONTH = min(EVENT_MONTH)) %>%
  ungroup() %>%
  group_by(CASE_START_MONTH, CASE_TYPE_EN, PRODUCT_LINE) %>%
  summarize(CASES = n_distinct(CASE_ID),
            EVENTS = n()) %>%
  ungroup() %>%
  mutate(EVENT_PER_CASE = EVENTS/CASES) %>% 
  # Plot
  ggplot(aes(x = substr(as.character(CASE_START_MONTH), 1, 7), group = 1)) +
  geom_line(aes(y = CASES, colour = "CASES"), size = 0.8) +
  geom_line(aes(y = EVENTS, colour = "EVENTS"), size = 0.8) +
  scale_y_continuous(label = unit_format(unit = "K", scale = 1e-3)) +
  theme(axis.text.x = element_text(angle = 90, size = 6)) +
  facet_grid(CASE_TYPE_EN~PRODUCT_LINE, labeller = label_wrap_gen(width=10)) +
  labs(
    x = "Month",
    y = "Count",
    title = "Number of Cases and Events per Month"
  )
```

## Number of Interactions

```{r}
t_ccc_pa %>%
  # Transform data
  filter(PRODUCT_LINE != "UNKNOWN") %>% 
  mutate(EVENT_MONTH = floor_date(EVENT_END, unit = "month")) %>%
  group_by(CASE_ID, CASE_TYPE_EN, PRODUCT_LINE) %>%
  mutate(CASE_START_MONTH = min(EVENT_MONTH)) %>%
  ungroup() %>%
  group_by(CASE_START_MONTH, CASE_TYPE_EN, PRODUCT_LINE) %>%
  summarize(CASES = n_distinct(CASE_ID),
            EVENTS = n()) %>%
  ungroup() %>%
  mutate(EVENT_PER_CASE = EVENTS/CASES) %>% 
  # Plot
  ggplot(aes(x = substr(as.character(CASE_START_MONTH), 1, 7), group = 1)) +
  geom_line(aes(y = EVENT_PER_CASE), size = 0.8) +
  theme(axis.text.x = element_text(angle = 90, size = 6)) +
  facet_grid(CASE_TYPE_EN~PRODUCT_LINE, labeller = label_wrap_gen(width=10)) +
  labs(
    x = "Month",
    y = "Count",
    title = "Number of Interactions per Case"
  )
```

## Volume Map of Request Types

```{r}
t_ccc_pa %>%
  # Transform data
  filter(PRODUCT_LINE != "UNKNOWN") %>% 
  mutate(EVENT_MONTH = floor_date(EVENT_END, unit = "month")) %>%
  group_by(CASE_ID, CASE_TYPE_EN, PRODUCT_LINE) %>%
  mutate(CASE_START_MONTH = min(EVENT_MONTH)) %>%
  ungroup() %>%
  group_by(CASE_START_MONTH, CASE_TYPE_EN, PRODUCT_LINE) %>%
  summarize(CASES = n_distinct(CASE_ID),
            EVENTS = n()) %>%
  ungroup() %>%
  mutate(EVENT_PER_CASE = EVENTS/CASES,
         SEGMENT = paste(PRODUCT_LINE, CASE_TYPE_EN)) %>%
  group_by(SEGMENT) %>%
  summarize(CASES = mean(CASES),
            EVENTS = mean(EVENTS),
            EVENTS_PER_CASE = mean(EVENT_PER_CASE)) %>% 
  ungroup() %>% 
  # Plot
  ggplot(aes(x = CASES, y = EVENTS_PER_CASE, label = SEGMENT)) +
    geom_point(aes(size = EVENTS), colour = "blue") +
    geom_label_repel(aes(label = SEGMENT),
                  box.padding   = 0.35, 
                  point.padding = 0.5,
                  segment.color = 'grey50') +
    coord_cartesian(ylim = c(0, 4.5)) +
    labs(
      x = "Cases (Monthly Average)",
    y = "Interactions per Case (Monthly Average)",
    title = "Volume Map of Major Request Types"
    )
```

## Channel Map of Request Types

```{r}
t_ccc_pa %>%
  # Transform data
  filter(PRODUCT_LINE != "UNKNOWN") %>% 
  mutate(EVENT_MONTH = floor_date(EVENT_END, unit = "month")) %>%
  group_by(CASE_ID, CASE_TYPE_EN, PRODUCT_LINE, EVENT_CHANNEL) %>%
  mutate(CASE_START_MONTH = min(EVENT_MONTH)) %>%
  ungroup() %>%
  group_by(CASE_START_MONTH, CASE_TYPE_EN, PRODUCT_LINE, EVENT_CHANNEL) %>%
  summarize(CASES = n_distinct(CASE_ID),
            EVENTS = n()) %>%
  ungroup() %>%
  mutate(EVENT_PER_CASE = EVENTS/CASES,
         SEGMENT = paste(PRODUCT_LINE, CASE_TYPE_EN)) %>%
  group_by(PRODUCT_LINE, CASE_TYPE_EN, SEGMENT, EVENT_CHANNEL) %>%
  summarize(CASES = mean(CASES),
            EVENTS = mean(EVENTS),
            EVENTS_PER_CASE = mean(EVENT_PER_CASE)) %>% 
  ungroup() %>% 
  # Plot
  ggplot(aes(x = EVENT_CHANNEL, y = EVENTS)) +
    geom_bar(stat = "identity") +
    theme(axis.text.x = element_text(angle = 90)) +
    #scale_y_continuous(label = unit_format(unit = "K", scale = 1e-3)) +
    #coord_flip() +
    facet_grid(PRODUCT_LINE ~ CASE_TYPE_EN) +
    labs(
      x = "Channel",
    y = "Interactions (Monthly Average)",
    title = "Channel Map of Major Request Types"
    )
```


## Impact Map by Channel

```{r, fig.width=14, fig.height=14}
t_ccc_pa %>%
  # Transform data
  filter(PRODUCT_LINE != "UNKNOWN") %>% 
  mutate(EVENT_MONTH = floor_date(EVENT_END, unit = "month")) %>%
  group_by(CASE_ID, CASE_TYPE_EN, PRODUCT_LINE) %>%
  mutate(CASE_START_MONTH = min(EVENT_MONTH)) %>%
  ungroup() %>%
  group_by(CASE_START_MONTH, CASE_TYPE_EN, PRODUCT_LINE, EVENT_CHANNEL) %>%
  summarize(CASES = n_distinct(CASE_ID),
            EVENTS = n()) %>%
  ungroup() %>%
  mutate(EVENT_PER_CASE = EVENTS/CASES,
         SEGMENT = paste(PRODUCT_LINE, CASE_TYPE_EN)) %>%
  group_by(SEGMENT, EVENT_CHANNEL) %>%
  summarize(CASES = mean(CASES),
            EVENTS = mean(EVENTS),
            EVENTS_PER_CASE = mean(EVENT_PER_CASE)) %>% 
  ungroup() %>% 
  # Plot
  ggplot(aes(x = CASES, y = EVENTS_PER_CASE, label = SEGMENT)) +
    geom_point(aes(size = EVENTS), colour = "blue") +
    geom_label_repel(aes(label = SEGMENT),
                      size = 3,
                      box.padding   = 0.35, 
                      point.padding = 0.5,
                      segment.color = 'grey50') +
    coord_cartesian(ylim = c(0, 4.5)) +
    labs(
      x = "Cases (Monthly Average)",
    y = "Interactions per Case (Monthly Average)",
    title = "Impact Map of Major Request Types by Channel"
    ) +
    facet_wrap(~EVENT_CHANNEL, ncol = 2)
```

***

# Identify Critical Interactions

```{r}
t_ccc_pa %>%
  # Transform data
  filter(PRODUCT_LINE != "UNKNOWN") %>%
  mutate(
    EVENT_MONTH = floor_date(EVENT_END, unit = "month"),
    ACTIVITY_EN = case_when(
    ACTIVITY_EN %in% c("Transmission", "Forward activity") ~ "Internal traffic activity",
    TRUE ~ ACTIVITY_EN
  )) %>%
  mutate(ACTIVITY_EN = forcats::fct_lump(factor(ACTIVITY_EN), n = 15)) %>%
  group_by(ACTIVITY_EN, EVENT_MONTH) %>% 
  summarize(COUNT = n()) %>% 
  ungroup() %>% 
  group_by(ACTIVITY_EN) %>% 
  summarize(COUNT = mean(COUNT)) %>% 
  ungroup() %>% 
  # Plor
  ggplot(aes(x = factor(ACTIVITY_EN, levels = unique(ACTIVITY_EN[order(COUNT)])), y = COUNT)) +
    geom_bar(stat = "identity") +
    scale_y_continuous(label = unit_format(unit = "K", scale = 1e-3)) +
    coord_flip() +
    labs(
      x = "Activity",
      y = "# of Activity (Monthly Average)",
      title = "Major Activity Types"
    )
```

## Interactions by Channel

```{r, fig.width=14, fig.height=14}
t_ccc_pa %>%
  # Transform data
  filter(PRODUCT_LINE != "UNKNOWN") %>%
  mutate(
    SEGMENT = paste(PRODUCT_LINE, CASE_TYPE_EN),
    EVENT_MONTH = floor_date(EVENT_END, unit = "month"),
    ACTIVITY_EN = case_when(
    ACTIVITY_EN %in% c("Transmission", "Forward activity") ~ "Internal traffic activity",
    TRUE ~ ACTIVITY_EN
  )) %>%
  mutate(ACTIVITY_EN = forcats::fct_lump(factor(ACTIVITY_EN), n = 10)) %>%
  # Filter out non-value adding or non-specific activities
  filter(!ACTIVITY_EN %in% c("Internal traffic activity", "Other")) %>% 
  group_by(SEGMENT, EVENT_CHANNEL, ACTIVITY_EN, EVENT_MONTH) %>% 
  summarize(COUNT = n()) %>% 
  ungroup() %>% 
  group_by(SEGMENT, ACTIVITY_EN, EVENT_CHANNEL) %>% 
  summarize(COUNT = mean(COUNT)) %>% 
  ungroup() %>% 
  # Plor
  ggplot(aes(x = factor(ACTIVITY_EN, levels = unique(ACTIVITY_EN[order(ACTIVITY_EN)])), y = COUNT)) +
    geom_bar(stat = "identity") +
    scale_y_continuous(label = unit_format(unit = "K", scale = 1e-3)) +
    coord_flip() +
    facet_grid(SEGMENT~EVENT_CHANNEL, labeller = label_wrap_gen(width=10)) +
    labs(
      x = "Activity",
      y = "# of Activity (Monthly Average)",
      title = "Major Activity Types"
    ) 
```