---
title: "Contact Center: Call Times and FTE"
author: "János Poór"
date: 'May 10, 2019'
output: rmdformats::readthedown
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, message=FALSE, warning=FALSE}
library(here)
library(dplyr)
library(ggplot2)
library(lubridate)
library(scales)
library(tidyr)
library(ggrepel)
```

```{r, message=FALSE, include=FALSE}
#########################################################################################
# Data Extraction #######################################################################
#########################################################################################

# Set JAVA_HOME, set max. memory, and load rJava library
Sys.setenv(JAVA_HOME = "C:\\Program Files\\Java\\jre1.8.0_171")
options(java.parameters = "-Xmx2g")
library(rJava)

# Output Java version
.jinit()
print(.jcall("java/lang/System", "S", "getProperty", "java.version"))

# Load RJDBC library
library(RJDBC)

# Get credentials
datamnr <-
  config::get("datamnr", file = "C:\\Users\\PoorJ\\Projects\\config.yml")

# Create connection driver
jdbcDriver <-
  JDBC(driverClass = "oracle.jdbc.OracleDriver", classPath = "C:\\Users\\PoorJ\\Desktop\\ojdbc7.jar")

# Open connection: kontakt---------------------------------------------------------------
jdbcConnection <-
  dbConnect(
    jdbcDriver,
    url = datamnr$server,
    user = datamnr$uid,
    password = datamnr$pwd
  )

# Fetch data
t_call_times <- dbGetQuery(jdbcConnection, 'select * from t_call_times')
t_mnap <- dbGetQuery(jdbcConnection, 'select * from t_mnap')

# Close db connection: kontakt
dbDisconnect(jdbcConnection)


# Transformations
t_call_times <- t_call_times %>% 
  mutate(EVENT_END = ymd_hms(EVENT_END)) %>% 
  filter(EVENT_END < as.Date('2019-01-01')) %>% 
  replace_na(list(PRODUCT_LINE = "UNKNOWN", PRODUCT_CODE = "UNKNOWN", CASE_TYPE_EN = "UNKNOWN"))

t_call_times[t_call_times$CASE_TYPE_EN == "Delete contract", "CASE_TYPE_EN"] <- "Contract termination"
t_call_times[t_call_times$CASE_TYPE_EN == "Claim report" &
           t_call_times$ACTIVITY_EN == "Provide information", "ACTIVITY_EN"] <- "Provide information Claim"
t_call_times[ t_call_times$ACTIVITY_EN == "!Delete contract", "ACTIVITY_EN"] <- "Delete contract"

t_mnap <- t_mnap %>% mutate(IDOSZAK = ymd_hms(IDOSZAK))
```

# 1. Glossary

* Call Volume: number of calls in period
* FTE: Full-time-equivalent computed for one month
* FTE_NORM: Normalized FTE - Full-time-equivalent computed for 1000 calls for one month


# 2. Call Volumes and FTE

```{r}
t_call_times %>%
  # Transform data
  #filter(PRODUCT_LINE != "UNKNOWN") %>% 
  mutate(EVENT_MONTH = floor_date(EVENT_END, unit = "month")) %>%
  group_by(EVENT_MONTH) %>%
  summarize(CALL_VOLUME = n(),
            CALL_TIME_SEC = sum(CALL_TIME)) %>%
  ungroup() %>%
  left_join(t_mnap, by = c("EVENT_MONTH" = "IDOSZAK")) %>% 
  mutate(FTE = CALL_TIME_SEC/60/60/7/MNAP,
         FTE_NORM = FTE/CALL_VOLUME*1000) %>%
  select(EVENT_MONTH, CALL_VOLUME, FTE, FTE_NORM) %>% 
  tidyr::gather(key = METRIC, value = VALUE, -EVENT_MONTH) %>% 
  # Plot
  ggplot(aes(x = substr(as.character(EVENT_MONTH), 1, 7), y = VALUE, group = 1)) +
  geom_line() +
  theme(axis.text.x = element_text(angle = 90)) +
  facet_grid(METRIC~., scales = "free") +
  labs(
    x = "Month",
    y = "Value",
    title = "Call Volumes and FTE"
  )
```


***

# 3. Understanding FTE across Request Types & Products

## 3.1. Breakdown of Volumes and FTE across Request Types

```{r, fig.width=14, fig.height=10}
t_call_times %>%
  # Transform data
  filter(PRODUCT_LINE != "UNKNOWN") %>% 
  mutate(EVENT_MONTH = floor_date(EVENT_END, unit = "month"),
         EVENT_QUARTER = paste0(year(EVENT_END), " q", quarter(EVENT_END)), 
         CASE_TYPE_EN = forcats::fct_lump(factor(CASE_TYPE_EN), n = 7),
         SEGMENT = CASE_TYPE_EN) %>%
  group_by(EVENT_MONTH, EVENT_QUARTER, SEGMENT) %>%
  summarize(CALL_VOLUME = n(),
            CALL_TIME_SEC = sum(CALL_TIME)) %>%
  ungroup() %>%
  left_join(t_mnap, by = c("EVENT_MONTH" = "IDOSZAK")) %>% 
  group_by(EVENT_QUARTER, SEGMENT) %>% 
  summarize(CALL_VOLUME = sum(CALL_VOLUME),
            CALL_TIME_SEC = sum(CALL_TIME_SEC),
            MNAP = sum(MNAP)) %>% 
  ungroup() %>% 
  mutate(FTE = CALL_TIME_SEC/60/60/7/MNAP,
         FTE_NORM = FTE*3/CALL_VOLUME*1000) %>%
  select(EVENT_QUARTER, SEGMENT, CALL_VOLUME, FTE, FTE_NORM) %>% 
  tidyr::gather(key = METRIC, value = VALUE, -EVENT_QUARTER, -SEGMENT) %>% 
  # Plot
  ggplot(aes(x = substr(as.character(EVENT_QUARTER), 1, 7), y = VALUE, group = 1)) +
  geom_line() +
  theme(axis.text.x = element_text(angle = 90),
        strip.text.x = element_text(angle=90),
        strip.text.y = element_text(angle=0)) +
  facet_grid(METRIC~SEGMENT, scales = "free") +
  labs(
    x = "Month",
    y = "Value",
    title = "Call Volumes and FTE by Request Types (Quarterly Trends)"
  )
```


## 3.2. Breakdown of Volumes and FTE across Request Types & Products

```{r, fig.width=14, fig.height=10}
t_call_times %>%
  # Transform data
  filter(PRODUCT_LINE != "UNKNOWN") %>% 
  mutate(EVENT_MONTH = floor_date(EVENT_END, unit = "month"),
         EVENT_QUARTER = paste0(year(EVENT_END), " q", quarter(EVENT_END)), 
         CASE_TYPE_EN = forcats::fct_lump(factor(CASE_TYPE_EN), n = 7),
         SEGMENT = paste(CASE_TYPE_EN, PRODUCT_LINE)) %>%
  group_by(EVENT_MONTH, EVENT_QUARTER, SEGMENT) %>%
  summarize(CALL_VOLUME = n(),
            CALL_TIME_SEC = sum(CALL_TIME)) %>%
  ungroup() %>%
  left_join(t_mnap, by = c("EVENT_MONTH" = "IDOSZAK")) %>% 
  group_by(EVENT_QUARTER, SEGMENT) %>% 
  summarize(CALL_VOLUME = sum(CALL_VOLUME),
            CALL_TIME_SEC = sum(CALL_TIME_SEC),
            MNAP = sum(MNAP)) %>% 
  ungroup() %>% 
  mutate(FTE = CALL_TIME_SEC/60/60/7/MNAP,
         FTE_NORM = FTE*3/CALL_VOLUME*1000) %>%
  select(EVENT_QUARTER, SEGMENT, CALL_VOLUME, FTE, FTE_NORM) %>% 
  tidyr::gather(key = METRIC, value = VALUE, -EVENT_QUARTER, -SEGMENT) %>% 
  # Plot
  ggplot(aes(x = substr(as.character(EVENT_QUARTER), 1, 7), y = VALUE, group = 1)) +
  geom_line() +
  theme(axis.text.x = element_text(angle = 90, size = 6),
        strip.text.x = element_text(angle=90),
        strip.text.y = element_text(angle=0)) +
  facet_grid(METRIC~SEGMENT, scales = "free") +
  labs(
    x = "Month",
    y = "Value",
    title = "Call Volumes and FTE by Request Types and Product (Quarterly Trends)"
  )
```

***


# 4. FTE Impact Map


## 4.1. Identify the Most Resource Intensive Segments

```{r}
t_call_times %>%
  # Transform data
  filter(PRODUCT_LINE != "UNKNOWN",
         EVENT_END >= as.Date('2018-01-01')) %>% 
  mutate(EVENT_MONTH = floor_date(EVENT_END, unit = "month"),
         #CASE_TYPE_EN = forcats::fct_lump(factor(CASE_TYPE_EN), n = 7),
         SEGMENT = forcats::fct_lump(paste(CASE_TYPE_EN, PRODUCT_LINE), n = 13, other_level = "Everything else")) %>%
  group_by(EVENT_MONTH,  SEGMENT) %>%
  summarize(CALL_VOLUME = n(),
            CALL_TIME_SEC = sum(CALL_TIME)) %>%
  ungroup() %>%
  left_join(t_mnap, by = c("EVENT_MONTH" = "IDOSZAK")) %>% 
  mutate(FTE = CALL_TIME_SEC/60/60/7/MNAP,
         FTE_NORM = FTE/CALL_VOLUME*1000) %>%
  # Compute monthly averages
  group_by(SEGMENT) %>% 
  summarize(
            CALL_VOLUME = mean(CALL_VOLUME),
            FTE = mean(FTE),
            FTE_NORM = mean(FTE_NORM)) %>% 
  # Plot
  ggplot(aes(x = CALL_VOLUME, y = FTE_NORM, label = SEGMENT)) +
    geom_point(aes(size = FTE), colour = "blue") +
    geom_label_repel(aes(label = SEGMENT),
                  box.padding   = 0.2, 
                  point.padding = 0.5,
                  segment.color = 'grey50') +
    #coord_cartesian(ylim = c(0, 4.5)) +
    labs(
      x = "Calls (Monthly Average)",
    y = "Normalized FTE (FTE for 1000 calls)",
    title = "FTE Impact Map of Calls"
    )
```


## 4.2. Understanding the Root-Causes of FTE comsumption

```{r, fig.width=14, fig.height=14}
t_call_times %>%
  # Transform data
  filter(PRODUCT_LINE != "UNKNOWN",
         EVENT_END >= as.Date('2018-01-01')) %>% 
  mutate(EVENT_MONTH = floor_date(EVENT_END, unit = "month"),
         #CASE_TYPE_EN = forcats::fct_lump(factor(CASE_TYPE_EN), n = 7),
         SEGMENT = forcats::fct_lump(paste(CASE_TYPE_EN, PRODUCT_LINE), n = 13)) %>%
  group_by(EVENT_MONTH, SEGMENT) %>% 
  mutate(ACTIVITY_EN = as.character(forcats::fct_lump(ACTIVITY_EN, prop = 0.05))) %>% 
  ungroup() %>% 
  group_by(EVENT_MONTH, SEGMENT, ACTIVITY_EN) %>%
  summarize(CALL_VOLUME = n(),
            CALL_TIME_SEC = sum(CALL_TIME)) %>%
  ungroup() %>%
  left_join(t_mnap, by = c("EVENT_MONTH" = "IDOSZAK")) %>% 
  mutate(FTE = CALL_TIME_SEC/60/60/7/MNAP,
         FTE_NORM = FTE/CALL_VOLUME*1000) %>%
  # Compute monthly averages
  group_by(SEGMENT, ACTIVITY_EN) %>% 
  summarize(
            CALL_VOLUME = mean(CALL_VOLUME),
            FTE = mean(FTE),
            FTE_NORM = mean(FTE_NORM)) %>% 
  tidyr::gather(-SEGMENT, -ACTIVITY_EN, key = METRIC, value = VALUE) %>% 
  # Plot
  ggplot(aes(x = ACTIVITY_EN, y = VALUE)) +
    geom_bar(stat = "identity") +
    theme(strip.text.y = element_text(angle=0)) +
    coord_flip() +
    facet_grid(SEGMENT~METRIC, scales = "free") +
    labs(
      x = "Calls types",
    y = "Values",
    title = "Call Types Comparison"
    )
```

